---
title: "bolivia_da_layers"
author: "Katherine Siegel"
date: "October 24, 2019"
output: html_document
---

## Description
New layers for Bolivia DINAMICA, as identified by discourse analysis

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
library(lwgeom)
library(sp)
# library(stars)
```

## Carrasco & Amboro
```{r}
### Open shp
ambcar <- st_read("D:/dinamica/bolivia_dinamica_data/AmbCar_Buffer_9_27/Bol_buffer.shp") %>%
  st_transform(., crs = 102033)

### Open raster
ambcar_rast <- raster("D:/dinamica/bolivia_dinamica_data_9_27/bol_2018_class.tif")

### Make big shp buffer for intersections
ambcar_big <- st_buffer(ambcar, dist = 50000)

# ### Save big ambcar
# st_write(ambcar_big,
#          "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/AmbCar/ambcar_large_buff.shp")

### Get municipios
### Municipios
bolivia <- getData("GADM", country = "BOL", level = 3) %>%
  st_as_sf() %>%
  st_transform(., crs = 102033) %>%
  filter(., NAME_1 %in% c("Cochabamba", 
                          "Santa Cruz")) %>%
  dplyr::select(., department = NAME_1, 
                province = NAME_2,
                municipio = NAME_3,
                geometry)
# st_write(bolivia,
#          "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bol_provinces.shp")


```

### Classified rasters
Reprojected all classified rasters to 102033 in QGIS

## Field research
Locations of field research sites from published lit in Web of Science (searched "Amboro" and "Carrasco" [2 separate searches], pulled out lat/long of research sites, made kmz in Google Earth, then converted to shp in ArcGIS)
```{r}
### Open shp and reproject
f_r <- st_read("D:/dinamica/bolivia_dinamica_data/field_research_site/ambcar_research.shp") %>%
  st_transform(., 102033) 

### Add column for field research site ID
f_r <- f_r %>%
  mutate(., fr_site = 1:nrow(f_r)) %>%
  dplyr::select(., fr_site, geometry)

### Intersect field research sites and ambcar_big
f_r <- st_intersection(f_r, ambcar_big)

### Write out so can calculate distance raster in Arc
st_write(f_r, 
         "D:/dinamica/bolivia_dinamica_data/field_research_site/ambcar_field_research.shp")

### Make distance raster in ArcGIS. Set max dist to 79000, export as tif: jam_dist_fr.tif

### Open tif
fr_dist <- raster("D:/dinamica/bolivia_dinamica_data/field_research_site/ac_dist_fr.tif")

### Resample to match Jaman raster
fr_resample <- raster::resample(fr_dist, ambcar_rast, "bilinear")

### Save output raster to folder on ext hard drive
writeRaster(fr_resample,
            filename = "D:/dinamica/bolivia_dinamica_data/discourse_analysis_final_layers/ac_dist_fr.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## Fires
```{r}
### Open fire dataset
fires <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/fires98_18/Fuegos98_18.shp")

### Make column for year
fires <- fires %>%
  mutate(year = year(DataHora))

### Keep fires from 5 years before time series through end of time series (2003-2018)
fires <- filter(fires, year > 2002)

### Transform crs
fires <- st_transform(fires, crs = 102033)

### Intersect fires and ambcar_big
fires_ac <- st_intersection(fires, ambcar_big)

### Save sf for making 1) distance and 2) density map in Arc
st_write(fires_ac, 
         "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/fires98_18/fires_2003_2018_ac.shp")

### For distance to fire, set max dist to 13500
### Save raster: bol_dist_fires.tif

### For fire density, used Point Density tool
### Use radius = 1000 (unit = map) --> fire_dens
### Map unit = square meter, set output to sq km units
### Save raster: bol_fire_density.tif
```

### Resample rasters
```{r}
### Open rasters
dist_fires <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_dist_fire.tif")
dens_fires <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_fire_density.tif")

### Resample to match ambcar raster
fire_dist_resample <- raster::resample(dist_fires, 
                                       ambcar_rast, 
                                       "bilinear")
fire_dens_resample <- raster::resample(dens_fires,
                                       ambcar_rast,
                                       "bilinear")

### Save output rasters to folder
writeRaster(fire_dist_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_fire_dist_re.tiff",
            format = "GTiff",
            overwrite = TRUE)
writeRaster(fire_dens_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_fire_dens_re.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## Distance to urban areas
Reclassify classified raster in ArcGIS to have a raster with urban areas (every other class = NoData)--> bol_08_urb_r.tif; bol_18_urb_r.tif

Then calculate distance to 2008 urban areas using Euclidean distance tool, set max distance to 11500 --> bol_d_urb.tif

Then resample to match ambcar
```{r}
### Open rasters
dist_urb <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bol_d_urb.tif")

### Resample to match ambcar raster
dist_urb_resample <- raster::resample(dist_urb, 
                                      ambcar_rast, 
                                      "bilinear")

### Save output rasters to folder
writeRaster(dist_urb_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_urban_dist_re.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## Distance to ag
Reclassify classified raster in ArcGIS to have a raster with ag areas (every other class = NoData)--> bol_08_ag_r.tif; bol_18_ag_r.tif

Then calculate distance to 2008 ag areas using Euclidean distance tool, set max distance to 8000 --> bol_dist_ag.tif
Then resample to match ambcar
```{r}
### Open rasters
dist_ag <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bol_dist_ag.tif")

### Resample to match ambcar raster
dist_ag_resample <- raster::resample(dist_ag, 
                                     ambcar_rast, 
                                     "bilinear")

### Save output rasters to folder
writeRaster(dist_ag_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_ag_dist_re.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## Illegal mines
## Illegal mining
Illegal mining across Amazon, from https://www.amazoniasocioambiental.org/es/mapas/#descargas. Three files: points, lines, polygons. Open here and combine into single shp, except leave out lines because lines are never the closest location to study areas and cause gdal issues.

Only need polygons for Bolivia
```{r}
### Open polys
min_po <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/MineriaIlegal/MineriaIlegal_pol.shp") %>%
  st_transform(., crs = 102033) %>%
  filter(., país %in% c("Brasil", "Perú", "Bolivia"))

### Write out
st_write(min_po,
         "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/mineria_ilegal.shp")

### Make distance raster in ArcGIS using larger buffer as processing extent --> bol_dist_illegal_min.tif

### Open distance raster
bol_illegal_min <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bol_dist_illegal_min.tif")

### Resample to match ambcar raster
dist_illegal_min_resample <- raster::resample(bol_illegal_min, 
                                              ambcar_rast, 
                                              "bilinear")

### Save output rasters to folder
writeRaster(dist_illegal_min_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_dist_illegal_mining.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## Distance to hotels
Eva's methods for hotels kml included: tourism=hotel, hostel, motel, guest house, apartment, chalet 
Hotels kml: Bolivia_hotels_etc.kml. Open in Arc and convert to shapefile --> bol_hotels.shp
```{r}
### Open bol_hotels and change crs
bol_hotels <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bol_hotels.shp") %>%
  st_transform(., crs = 102033)

### Drop z dimension
bol_hotels <- st_zm(bol_hotels)

### Write out for Euclidean distance layer
st_write(bol_hotels, 
         "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bol_hotels_102033.shp")

### Set max distance to 50,000 --> bol_dist_hotel.tif

### Open distance raster
dist_hotel <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bol_dist_hotel.tif")

### Resample to match ambcar raster
dist_hotel_resample <- raster::resample(dist_hotel, 
                                        ambcar_rast, 
                                        "bilinear")

### Save output rasters to folder
writeRaster(dist_hotel_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_dist_hotels.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## Distance to tourism attractions and hotels
List of tourism attractions from management plan (Amboro only) and from SERNAP website (http://sernap.gob.bo/amboro/; http://sernap.gob.bo/carrasco/atractivos-turisticos/). Find points in Google Earth, export as kml ("Amboro tourism"). Open in ArcGIS and save as .shp. --> ambcar_tourism.shp
```{r}
### Open tourist attractions file and convert to 102033
tour <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/ambcar_tourism.shp") %>%
  st_transform(., crs = 102033)

### Open bol_hotels and change crs
bol_hotels <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bol_hotels.shp") %>%
  st_transform(., crs = 102033)

### Drop z dimension from both
tour <- st_zm(tour)
bol_hotels <- st_zm(bol_hotels)

### rbind
bol_tourism <- rbind(tour, bol_hotels)

### Write out for Euclidean distance layer
st_write(bol_tourism, 
         "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bolivia_tourism.shp")

### bol_dist_tourism.tif in ArcMap
bol_tourism_dist <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/bol_dist_tourism.tif")

### Resample to match ambcar raster
dist_tour_resample <- raster::resample(bol_tourism_dist, 
                                       ambcar_rast, 
                                       "bilinear")

### Save output rasters to folder
writeRaster(dist_tour_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_dist_tourism.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## Precip
File from Eva (GEE), reprojected to 102033 in gdal
gdalwarp -t_srs EPSG:102033 -r bilinear PPTAmbCar.tif ppt_ambcar_102033.tif
```{r}
### Open raster
precip <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/ppt_ambcar_102033.tif")

### Resample to match ambcar raster
precip_resample <- raster::resample(precip, 
                                    ambcar_rast, 
                                    "bilinear")

### Save output rasters to folder
writeRaster(precip_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_ppt.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## Soil moisture
```{r}
### Open raster
soil <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/sm_ambcar_102033.tif")

### Resample to match ambcar raster
soil_resample <- raster::resample(soil, 
                                  ambcar_rast, 
                                  "bilinear")

### Save output rasters to folder
writeRaster(soil_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_soil.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## DEM layers
Resample DEM layers to match new Bolivia raster/shp
```{r}
### Open rasters
bol_elev <- raster("D:/dinamica/processed_layers/dem_ambcar_102033.tif")
bol_slope <- raster("D:/dinamica/processed_layers/slope_ambcar.tif")
bol_aspect <- raster("D:/dinamica/processed_layers/aspect_ambcar.tif")

### Resample to match new PA extent
elev_resample <- raster::resample(bol_elev, 
                                  ambcar_rast, 
                                  "bilinear")
slope_resample <- raster::resample(bol_slope, 
                                   ambcar_rast, 
                                   "bilinear")
aspect_resample <- raster::resample(bol_aspect, 
                                    ambcar_rast, 
                                    "bilinear")

### Save output rasters to folder
writeRaster(elev_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_elev.tiff",
            format = "GTiff",
            overwrite = TRUE)
writeRaster(slope_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_slope.tiff",
            format = "GTiff",
            overwrite = TRUE)
writeRaster(aspect_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_aspect.tiff",
            format = "GTiff",
            overwrite = TRUE)
```


## REDD Projects
Data sources: 
1. Global Comparative Study on REDD+; Department of Forestry and Environmental Resources, 2017, "Global Database of REDD+ and Other Forest Carbon Projects", https://doi.org/10.17528/CIFOR/DATA.00059, Center for International Forestry Research (CIFOR), V1
https://data.cifor.org/dataset.xhtml?persistentId=doi:10.17528/CIFOR/DATA.00059
* data through 2011  
2. International Database on REDD+ projects and programs. CIFOR 2015. http://www.reddprojectsdatabase.org/.  
3. Institute for Global Environmental Strategies. 2013. REDD+ Online Database. http://redd-database.iges.or.jp/redd/.

Assemble list of REDD projects:  
* Cochabamba (CIFOR 2017)-- not in study area (according to map from Forest Trends)  
* Sub-national REDD in the Bolivian Amazon (CIFOR 2017)  
* Biodiversity Conservation at the Landscape Scale: Greater Madidi Landscape Conservation Area (CIFOR 2017)-- not in study area  
* Carbon Sequestration Through Reforestation In The Bolivian Tropics By Smallholders (CIFOR 2017)-- part of AR Bolivia  
* CI-Pillon (CIFOR 2017)-- no info on this  
* Project by the Centro de Investigacion y Desarrollo Regional (CIDRE) (CIFOR 2017)  
* Rio Comarapa forestation and reforestation with the Fundacion Amigos de la Naturaleza (FAN) (CIFOR 2017)  
* Noel Kempff Mercado Climate Action Project (CIFOR 2015)-- not close to AmbCar
* Protection of the Bolivian Amazon Forest (CIFOR 2015)-- not close to AmbCar

Projects potentially in study area:  
* Sub-national REDD in the Bolivian Amazon (CIFOR 2017)  
* Carbon Sequestration Through Reforestation In The Bolivian Tropics By Smallholders (CIFOR 2017)-- part of AR Bolivia  
* Project by the Centro de Investigacion y Desarrollo Regional (CIDRE) (CIFOR 2017) * Rio Comarapa forestation and reforestation with the Fundacion Amigos de la Naturaleza (FAN) (CIFOR 2017)   


### CIFOR 2017
```{r}
# ### Open CIFOR database
# redd <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica_nov2/redd/GCS_Project_Count.shp")
# 
# ### Subset to Bolivia
# redd_bol <- subset(redd, CNTRY_NAME == "Bolivia")
### Doesn't actually have shapefile for the individual projects

### Accompanying excel file lists Bolivia REDD projects.
redd_excel <- read_csv("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica_nov2/redd/GCSProjectInfo.csv") %>%
  subset(., Country == "Bolivia")
```

## Other PES 
Sources 
* Forest Trends. Forest Carbon Portal. https://www.forest-trends.org/project-list/#project-action

### Forest Trends  
* Comarapa-- in study area, Fundacion Natura Bolivia    
* El Chape, Mairana-- in study area, Fundacion Natura Bolivia, nigelasquith@naturabolivia.org  
* Santa Cruz (Fonacruz)-- in study area, Fundacion Natura Bolivia, nigelasquith@naturabolivia.org    
* Vallegrande-- in study area, Fundacion Natura Bolivia, nigelasquith@naturabolivia.org    
* Santa Rosa de Lima, Los Negros  -- in study area, Fundacion Natura Bolivia, nigelasquith@naturabolivia.org    
* ArBolivia Phase 1-- Cochabamba  
* ArBolivia Phase 2-- not in study area  

### Verra Project Database  
* Protection of the Bolivian Amazon Forest (not in study area)

### Projects in study area
* Comarapa-- in study area, Fundacion Natura Bolivia    
* El Chape, Mairana-- in study area, Fundacion Natura Bolivia, nigelasquith@naturabolivia.org  
* Santa Cruz (Fonacruz)-- in study area, Fundacion Natura Bolivia, nigelasquith@naturabolivia.org    
* Vallegrande-- in study area, Fundacion Natura Bolivia, nigelasquith@naturabolivia.org    
* Santa Rosa de Lima, Los Negros  -- in study area, Fundacion Natura Bolivia, nigelasquith@naturabolivia.org    
* ArBolivia Phase 1-- Cochabamba  

