---
title: "bolivia_da_layers"
author: "Katherine Siegel"
date: "October 24, 2019"
output: html_document
---

## Description
New layers for Bolivia DINAMICA, as identified by discourse analysis

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
library(lwgeom)
library(sp)
# library(stars)
```

## Carrasco & Amboro
```{r}
### Open shp
ambcar <- st_read("D:/dinamica/bolivia_dinamica_data/AmbCar_Buffer_9_27/Bol_buffer.shp") %>%
  st_transform(., crs = 102033)

### Open raster
ambcar_rast <- raster("D:/dinamica/bolivia_dinamica_data_9_27/bol_2018_class.tif")

### Make big shp buffer for intersections
ambcar_big <- st_buffer(ambcar, dist = 50000)

```

## Field research
Locations of field research sites from published lit in Web of Science (searched "Amboro" and "Carrasco" [2 separate searches], pulled out lat/long of research sites, made kmz in Google Earth, then converted to shp in ArcGIS)
```{r}
### Open shp and reproject
f_r <- st_read("D:/dinamica/bolivia_dinamica_data/field_research_site/ambcar_research.shp") %>%
  st_transform(., 102033) 

### Add column for field research site ID
f_r <- f_r %>%
  mutate(., fr_site = 1:nrow(f_r)) %>%
  dplyr::select(., fr_site, geometry)

### Intersect field research sites and ambcar_big
f_r <- st_intersection(f_r, ambcar_big)

### Write out so can calculate distance raster in Arc
st_write(f_r, 
         "D:/dinamica/bolivia_dinamica_data/field_research_site/ambcar_field_research.shp")

### Make distance raster in ArcGIS. Set max dist to 79000, export as tif: jam_dist_fr.tif

### Open tif
fr_dist <- raster("D:/dinamica/bolivia_dinamica_data/field_research_site/ac_dist_fr.tif")

### Resample to match Jaman raster
fr_resample <- raster::resample(fr_dist, ambcar_rast, "bilinear")

### Save output raster to folder on ext hard drive
writeRaster(fr_resample,
            filename = "D:/dinamica/bolivia_dinamica_data/discourse_analysis_final_layers/ac_dist_fr.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

## REDD Projects
Global Comparative Study on REDD+; Department of Forestry and Environmental Resources, 2017, "Global Database of REDD+ and Other Forest Carbon Projects", https://doi.org/10.17528/CIFOR/DATA.00059, Center for International Forestry Research (CIFOR), V1
https://data.cifor.org/dataset.xhtml?persistentId=doi:10.17528/CIFOR/DATA.00059
* data through 2011
```{r}
### Open CIFOR database
redd <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica_nov2/redd/GCS_Project_Count.shp")

### Subset to Bolivia
redd_bol <- subset(redd, CNTRY_NAME == "Bolivia")

### Accompanying excel file lists several more Bolivia REDD projects.
redd_excel <- read_csv("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica_nov2/redd/GCSProjectInfo.csv") %>%
  subset(., Country == "Bolivia")

redd_excel$Project
```

