---
title: "brazil_da_layers"
author: "Katherine Siegel"
date: "October 14, 2019"
output: html_document
---

## Description
New layers for Brazil DINAMICA, as identified by discourse analysis

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
library(lwgeom)
library(sp)
# library(stars)
```

## Jamanxim
```{r}
### Open Jamanxim shp
jambuf <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/JamanBuffer/JamanBuffer.shp") %>%
  st_transform(., crs = 102033) # %>%
  # st_write(., "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/JamanBuffer/JamanBuffer_reproj.shp")

### Open raster
jm_2008 <- raster("D:/dinamica/brazil_simple/data/unsuper_bra_2008_dry_102033.tif")

### Municipios
braz <- getData("GADM", country = "BRA", level = 2) %>%
  st_as_sf() %>%
  st_transform(., crs = 102033) %>%
  subset(., NAME_1 == "Pará") %>%
  dplyr::select(., state = NAME_1, 
                municipio = NAME_2,
                geometry)

### Muncipios in Jamanxim
munic_jam <- st_intersection(jambuf, braz)

### Make sf of muncipios in Jamanxim
municipios <- braz %>%
  filter(., municipio %in% munic_jam$municipio)
```

## Proposed Infrastructure
Coordinates of proposed dams and railroads from Stefano Wrobleski 

### Railroad
Data from http://infraestrutura.gov.br/images/BIT_TESTE/kmz/ferrovias.kmz. Converted kmz to shp in ArcMap (KML to Layer function)
```{r}
### Open shapefile of railroads
rr <- st_read("D:/dinamica/brazil_dinamica_data/proposed_infrastr/ferrovias.shp") %>%
  st_transform(., crs = 102033)

### Make larger Jaman buffer for clipping
jam_big <- st_buffer(jambuf, dist = 50000)

### Intersect roads and jaman buff
rr <- st_intersection(rr, jam_big)

### Write out so can calculate distance raster in Arc
st_write(rr, 
         "D:/dinamica/brazil_dinamica_data/proposed_infrastr/railroads.shp")
st_write(jam_big, "D:/dinamica/brazil_dinamica_data/jaman_bigbuff.shp")

### Set max dist to 138000, export as tif: dist_rr.tif

### Open tif
rr_dist <- raster("D:/dinamica/brazil_dinamica_data/proposed_infrastr/dist_rr.tif")

### Resample to match Jaman raster
rr_resample <- raster::resample(rr_dist, jm_2008, "bilinear")

### Save output raster to folder on ext hard drive
writeRaster(rr_resample,
            filename = "D:/dinamica/brazil_dinamica_data/discourse_analysis_final_layers/bra_dist_proposed_rr.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

### Dams
Data from Agência Nacional de Energia Elétrica:  
* Cachoeira dos Patos: 5d54m59sS 55d45m36sW  
* Jardim de Ouro:  6d15m49sS 55d45m53sW  
* Jamanxim: 5d38m48sS 55d52m38sW
```{r}
### Dam vectors
dam_names <- c("Cachoeira dos Patos", "Jardim de Ouro", "Jamanxim")
dam_coords <- c("5d54m59r S", "55d45m36r W", "6d15m49r S", "55d45m53r W",
                "5d38m48r S", "55d52m38r W")

### Convert dam_coords to DMS
dam_coords_dd <- as.numeric(char2dms(from = dam_coords, chd = "d", 
                                     chm = "m", chs = "r"))

### Make sf for each dam
cdp_sf <- st_point()

### Make vectors for df
lat_dams <- c(dam_coords_dd[1], dam_coords_dd[3], dam_coords_dd[5])
lon_dams <- c(dam_coords_dd[2], dam_coords_dd[4], dam_coords_dd[6])

### Make df
dams <- data.frame(cbind(dam_names, lat_dams, lon_dams))
dams$lat_dams <- as.numeric(as.character(dams$lat_dams))
dams$lon_dams <- as.numeric(as.character(dams$lon_dams))

### Convert to sf
dams_sf <- st_as_sf(x = dams, 
                    coords = c("lat_dams", "lon_dams"),
                    crs = 102033)

dam_names <- c("Cachoeira dos Patos", "Jardim de Ouro", "Jamanxim")

### CDP
cdp_sf <- data.frame(place = "Cachoeira dos Patos", 
       lat = dam_coords_dd[1], lon = dam_coords_dd[2])
cdp_sf <- st_as_sf(x = cdp_sf, coords = c("lon", "lat"), crs = 102033)


# ### Convert crs
# st_crs(dams_sf) <- 102033

### Write out to inspect
st_write(cdp_sf, "D:/dinamica/brazil_dinamica_data/proposed_infrastr/cdp_dam.shp")
```

## Head of cattle
Municipality-level data from 2017 Censo Agropecuario (https://censos.ibge.gov.br/agro/2017/templates/censo_agro/resultadosagro/pecuaria.html?localidade=15&tema=75652)
```{r}
### Open data
cattle <- read_csv("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/brazil/cattle.csv")

### Merge cattle with municipio geometries
cattle <- merge(cattle, braz, 
                by = "municipio",
                all.x = TRUE)
st_geometry(cattle) <- cattle$geometry

### Calculate municipio area (m2)
cattle$municipio_area_m2 <- st_area(cattle)

### Convert to numeric
cattle$municipio_area_m2 <- as.numeric(cattle$municipio_area_m2)

### Convert to municipality in km2
cattle$municipio_area_km2 <- cattle$municipio_area_m2/1000000

### Calculate cattle per km2
cattle <- cattle %>%
  mutate(cattle_km2 = cattle_head/municipio_area_km2)

### Drop excess columns
cattle <- cattle %>%
  dplyr::select(., municipio, cattle_km2, geometry) %>%
  st_write("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/brazil/cattle.shp")

### Convert to raster in gdal
### gdal_rasterize -a cattle_km2 -tr 30 30 cattle.shp cattle.tiff

### Open raster
cattle_rast <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/brazil/cattle.tiff")

### Resample to match LUC raster (bilinear)
cattle_resample <- raster::resample(cattle_rast, 
                                    jm_2008, "bilinear")

### Save output raster to folder on ext hard drive
writeRaster(cattle_resample,
            filename = "D:/dinamica/brazil_dinamica_data/discourse_analysis_final_layers/bra_cattle.tiff",
            format = "GTiff",
            overwrite = TRUE)

```

## Field research
Locations of field research sites from published lit in Web of Science (searched "Jamanxim," pulled out lat/long of research sites, made kmz in Google Earth, then converted to shp in ArcGIS)
```{r}
### Open shp and reproject
f_r <- st_read("D:/dinamica/brazil_dinamica_data/field_research_sites/jaman_research.shp") %>%
  st_transform(., 102033) 

### Add column for field research site ID
f_r <- f_r %>%
  mutate(., fr_site = 1:nrow(f_r)) %>%
  dplyr::select(., fr_site, geometry)

### Intersect field research sites and jaman buff
f_r <- st_intersection(f_r, jam_big)

### Write out so can calculate distance raster in Arc
st_write(f_r, 
         "D:/dinamica/brazil_dinamica_data/field_research_sites/jam_field_research.shp")

### Make distance raster in ArcGIS. Set max dist to 164400, export as tif: jam_dist_fr.tif

### Open tif
fr_dist <- raster("D:/dinamica/brazil_dinamica_data/field_research_sites/jam_dist_fr.tif")

### Resample to match Jaman raster
fr_resample <- raster::resample(fr_dist, jm_2008, "bilinear")

### Save output raster to folder on ext hard drive
writeRaster(fr_resample,
            filename = "D:/dinamica/brazil_dinamica_data/discourse_analysis_final_layers/jam_dist_fr.tif",
            format = "GTiff",
            overwrite = TRUE)
```

## Land tenure  
Background notes (Ezzine-de-Blas et al. 2011):  
* Brazilian Federal Land Reform began in 1964, National Institute for Agrarian Reform (INCRA)  
* projectos fundiarios: > 8500 settlements for landless peasants, mostly in Legal Amazon  

### INCRA files
```{r}
### Parcela Regularização
regular_parc <- st_read("D:/dinamica/brazil_dinamica_data/incra_land_tenure/Parcela Regularização_PA.shp") %>%
  st_transform(., crs = 102033)
### Modality: Electronic auction, Competition, Invitation
### Situacao: Non-titled, Registered, Titled but not registered, <NA>
### Status: Titling, Tax approval

### Immovel certificado SIGEF Total
immovel_sigef <- st_read("D:/dinamica/brazil_dinamica_data/incra_land_tenure/Sigef Brasil_PA.shp") %>%
  st_transform(., crs = 102033)
### Situacao: Non-titled, Registered, Titled but not registered, <NA>
### Status: Certified, Registered

### Immovel certificado SNCI Total  
immovel_snci <- st_read("D:/dinamica/brazil_dinamica_data/incra_land_tenure/Imóvel certificado SNCI Brasil_PA.shp") %>%
  st_transform(., crs = 102033)
### Certified

### Projectos de assentamento total
assentamento <- st_read("D:/dinamica/brazil_dinamica_data/incra_land_tenure/Assentamento Brasil_PA.shp") %>%
  st_transform(., crs = 102033)
```

#### Ag Reform Settlements
Locations of ag reform settlements within Jamanxim and buffer
```{r}
### Intersect ag reform settlements with jaman
assentamento_jaman <- st_intersection(assentamento,
                                       jambuf)

### There are 4 ag reform settlements that overlap with Jamanxim. All are classified as "assentamento criado."

assentamento_jaman$burn_in <- 1

### Write out the shp and then rasterize in gdal
assentamento_jaman %>% 
  dplyr::select(., burn_in, geometry) %>%
  st_write(., 
           "D:/dinamica/brazil_dinamica_data/incra_land_tenure/assent_jam.shp")

### Use gdal to rasterize: 
### gdal_rasterize -a burn_in -tr 30 30 assent_jam.shp assent_jam.tif

### Open tif from gdal
jaman_tif <- raster("D:/dinamica/brazil_dinamica_data/incra_land_tenure/assent_jam.tif")

### Resample to match Jamanxim raster (use "ngb" since binary settlement/nonsettlement)
jaman_resample <- raster::resample(jaman_tif, 
                                   jm_2008, 
                                   "ngb")

### Extend raster to match extent of Jamanxim
jaman_resample_lg <- raster::extend(jaman_resample,
                                    jm_2008,
                                    value = 0)

### Save output raster to folder on ext hard drive
writeRaster(jaman_resample_lg,
            filename = "D:/dinamica/brazil_dinamica_data/discourse_analysis_final_layers/bra_agreform_settlements.tiff",
            format = "GTiff",
            overwrite = TRUE)

### Clear old files
rm(jaman_resample, jaman_resample_lg, 
   assentamento, assentamento_jaman)
```

#### Land titling
```{r}
### Is there overlap between regular_parc and immovel_sigef?
### Crop both to Jamanxim municipios
parc_municipios <- st_intersection(regular_parc,
                              municipios) %>%
  dplyr::select(., parcela_co, situacao_i, status, 
                municipio, geometry)
sigef_municipios <- st_intersection(immovel_sigef,
                               municipios) %>%
  dplyr::select(., parcela_co, situacao_i, status, 
                municipio, geometry)
# ### Check overlap
# parc_sigef <- st_intersection(parc_municipios,
#                               sigef_municipios)
# ### There is some overlap in the areas

### Combine sf objects
parc_municipios$data <- "parc_municipios"
sigef_municipios$data <- "parc_sigef"
parc_sigef <- rbind(parc_municipios,
                    sigef_municipios)

### Subset to non-titled and nonregistered
nontitled <- subset(parc_sigef, 
                    situacao_i == "NAOTITULADA")

### Add area for geometries
nontitled$area <- st_area(nontitled$geometry)

### Sum area by municipio
area_per_mun <- nontitled %>%
  group_by(municipio) %>%
  summarise(total_area = sum(area)) %>%
  ungroup()

### Get area of total municipio
municipios$area <- st_area(municipios$geometry)

### Reduce columns
municipios <- municipios %>% 
  dplyr::select(., municipio, area)
st_geometry(area_per_mun) <- NULL
area_per_mun <- area_per_mun %>%
  dplyr::select(., municipio, total_area)

### Combine
area_per_mun <- merge(area_per_mun, municipios, 
                      by = "municipio")

### Calculate nontitled area per municipio
area_per_mun$proportion_nontitled <- area_per_mun$total_area/area_per_mun$area
area_per_mun$proportion_nontitled <- as.numeric(area_per_mun$proportion_nontitled)

### Resort columns
area_per_mun <- area_per_mun %>%
  dplyr::select(., proportion_nontitled, geometry)
st_geometry(area_per_mun) <- area_per_mun$geometry
st_write(area_per_mun, 
         "D:/dinamica/brazil_dinamica_data/incra_land_tenure/nontitled_para.shp")

### Use gdal to rasterize: 
### gdal_rasterize -a burn_in -tr 30 30 assent_jam.shp assent_jam.tif

# ### Intersect with Jamanxim
# area_per_mun_jam <- st_intersection(area_per_mun, jambuf)
# 
# ### Drop excess columns, then write out the shp to rasterize in gdal
# area_per_mun_jam <- area_per_mun_jam %>%
#   dplyr::select(., -area, -Type, -Area, -tp_uso,
#                 -nome, -Date, -Source) %>%
#   st_write(., "D:/dinamica/brazil_dinamica_data/incra_land_tenure/nontitled_jam.shp")

### Use gdal to rasterize: 
### gdal_rasterize -a burn_in -tr 30 30 assent_jam.shp assent_jam.tif


```

