---
author: "Katherine Siegel"
date: "February 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages
library(tidyverse)
library(sf)
library(RCurl)
library(fasterize)
library(raster)

# ### Set wd
# setwd("~/Documents/SESYNC/brazil_dinamica_data/popdens")
```

## Population density (2010)
I have data on population and population density for each municipio in Para state from the 2010 census: https://censo2010.ibge.gov.br/sinopse/index.php?uf=15&dados=8, "Sinopse do Censo Demografico 2010: Para," IBGE. "Tabela 2.1 - Populacao residente, total, urbana total e urbana na sede municipial, com indicacao da area total e densidade demografica, segundo as Unidades da Federacao e os municipios - 2010." Fonte: IBGE, Censo Demográfico 2010.

I also have shapefiles of the municipios from IBGE: http://mapasinterativos.ibge.gov.br/arcgis/rest/services/DPA2010/MapServer. "Divisão Pol????tico Administrativa: Municipios"

### Pop density data
```{r}
### Open csv of pop data
pd <- read_csv("~/Documents/SESYNC/dinamica/brazil_dinamica_data/popdens/pop_dens_data.csv")
pd <- pd[complete.cases(pd), ]
pd$municipio_uc <- toupper(pd$municipio)

### Fix punctuation in pop data
#### Drop "." in "total"
pd$total <- str_remove(pd$total, "[.]")
#### Convert total to numeric
pd$total <- as.numeric(pd$total)

### Fix municipio area
#### Divide area by 10 because read_csv dropped "," that is decimal point
pd$area_km2_corr <- pd$area_total_km2/10

### Fix population density data
#### Convert "," to "." and convert to numeric
pd$pop_dens_corr <- as.numeric(gsub(",", ".", pd$pop_dens_individ_km2))
```

### Merge with municipio polygons
```{r}
### Open shp of municipios
mcp <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/para_municipios.shp", 
               options = "ENCODING=latin1",
               stringsAsFactors = FALSE)

### Merge
mcp_pd <- merge(x = mcp, 
                y = pd, 
                by.x = "NM_MUNICIP", 
                by.y = "municipio_uc", 
                all = TRUE)

### Make simplified version for ESRI
mcp_pd <- dplyr::select(mcp_pd, 
                        municip = municipio,
                        pop = total,
                        area_km2 = area_km2_corr,
                        pd_km2 = pop_dens_corr,
                        geometry = geometry)


### Write sf
st_write(mcp_pd, 
         "~/Documents/SESYNC/dinamica/brazil_dinamica_data/para_pop_density.shp")
```

## Population density (2000)
I have data on population for each census sector in Para state from the 2000 census: https://www.ibge.gov.br/estatisticas-novoportal/sociais/educacao/9663-censo-demografico-2000.html?edicao=10192&t=resultados, "Censo Demografico 2000: Tabelas- Agregados por Setores Censitarios," IBGE. "Pessoa1_PA.csv" Fonte: IBGE, Censo Demografico 2000.

I also have shapefiles of the census sectors from IBGE. "Setores Censitarios 2000."
```{r}
### Open csv of pop data
pd_00 <- read_csv("~/Documents/SESYNC/dinamica/brazil_dinamica_data/popdens/census2000/Pessoa1_PA.csv")

### Column with population data is V1330 ("Pessoas (popula??o residente no setor) Nota: Esta vari?vel possui os mesmos valores da vari?vel V0237 [mirador]"). Cod_setor is the sector code
pd_00 <- select(pd_00, 
                cod_setor = Cod_setor,
                situacao = Situacao,
                tipo_do_setor = Tipo_do_setor,
                pop = V1330)
pd_00$cod_setor <- as.factor(as.character(pd_00$cod_setor))
```

### Convert municipios to raster 
```{r}
### Make empty raster
r <- raster(ncols = 100, nrow = 100)
mcp_r <- rasterize(mcp, r)
```


### Merge with sector data
```{r}
### Open shp of municipios
sect <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/popdens/census2000/setores/15SE500G.shp")
# sect <- st_read("para_setores_censitarios.shp", 
#                options = "ENCODING=latin1",
#                stringsAsFactors = FALSE)

### Merge
sect_pd <- merge(x = sect, 
                y = pd_00, 
                by.x = "CODIGO", 
                by.y = "cod_setor", 
                all.y = TRUE)

### Look at pops where sector = NA
sect_check_2 <- sect_pd[is.na(sect_pd$GEOCODIGO), ]

### Drop duplicate rows
st_geometry(sect_pd) <- NULL
sect_pd_unique <- sect_pd[!duplicated(sect_pd), ]

### Add geometry back in
sect_pd_unique <- merge(x = sect_pd_unique,
                        y = sect,
                        by = "CODIGO", 
                        all.x = TRUE)
```

There are 4127 reported population values without an associated sector in the shp

IBGE downloads not currently working. For now, I will calculate the pop density by municipio using what I have at the moment.
```{r}
### Group by municipio
mcp_summ <- as.data.frame(sect_pd) %>%
  group_by(NM_MUNICIP) %>%
  summarise(mcp_pop = sum(pop, na.rm = TRUE))

### 13469 outside of any municipio

### Merge with municipio area from pd (2010)
pd_area <- pd[]
mcp_summ <- merge(mcp_summ, 
                  pd[, c(5, 6)], 
                  by.x = "NM_MUNICIP", 
                  by.y = "municipio_uc") ## drops pop with no municip

### Calculate pd
mcp_summ$pop_dens <- mcp_summ$mcp_pop / mcp_summ$area_km2_corr

### Merge with shp
mcp_pd_00 <- merge(x = mcp, 
                   y = mcp_summ, 
                   by = "NM_MUNICIP", 
                   all = TRUE)

### Make simplified version for ESRI
mcp_pd_00 <- dplyr::select(mcp_pd_00, 
                           municip = NM_MUNICIP,
                           pop = mcp_pop,
                           area_km2 = area_km2_corr,
                           pd_km2 = pop_dens,
                           geometry = geometry)


### Write sf
st_write(mcp_pd_00, "~/Documents/SESYNC/dinamica/brazil_dinamica_data/popdens/para_pop_density_2000.shp")
```

