---
title: "brazil_da_layers"
author: "Katherine Siegel"
date: "October 14, 2019"
output: html_document
---

## Description
New layers for Brazil DINAMICA, as identified by discourse analysis

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
library(lwgeom)
library(sp)
# library(stars)
```

## Jamanxim
```{r}
### Open Jamanxim shp
jambuf <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/JamanBuffer/JamanBuffer.shp") %>%
  st_transform(., crs = 102033) %>%
  st_write(., "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/JamanBuffer/JamanBuffer_reproj.shp")

### Open raster
jm_2008 <- raster("D:/dinamica/brazil_simple/data/unsuper_bra_2008_dry_102033.tif")

### Municipios
braz <- getData("GADM", country = "BRA", level = 2) %>%
  st_as_sf() %>%
  st_transform(., crs = 102033) %>%
  subset(., NAME_1 == "Pará") %>%
  dplyr::select(., state = NAME_1, 
                municipio = NAME_2,
                geometry)
```

## Proposed Infrastructure
Coordinates of proposed dams and railroads from Stefano Wrobleski 

### Railroad
Data from http://infraestrutura.gov.br/images/BIT_TESTE/kmz/ferrovias.kmz. Converted kmz to shp in ArcMap (KML to Layer function)
```{r}
### Open shapefile of railroads
rr <- st_read("D:/dinamica/brazil_dinamica_data/proposed_infrastr/ferrovias.shp") %>%
  st_transform(., crs = 102033)

### Make larger Jaman buffer for clipping
jam_big <- st_buffer(jambuf, dist = 50000)

### Intersect roads and jaman buff
rr <- st_intersection(rr, jam_big)

### Write out so can calculate distance raster in Arc
st_write(rr, 
         "D:/dinamica/brazil_dinamica_data/proposed_infrastr/railroads.shp")
st_write(jam_big, "D:/dinamica/brazil_dinamica_data/jaman_bigbuff.shp")

### Set max dist to 138000, export as tif: dist_rr.tif

### Open tif
rr_dist <- raster("D:/dinamica/brazil_dinamica_data/proposed_infrastr/dist_rr.tif")

### Resample to match Jaman raster
rr_resample <- raster::resample(rr_dist, jm_2008, "bilinear")

### Save output raster to folder on ext hard drive
writeRaster(rr_resample,
            filename = "D:/dinamica/brazil_dinamica_data/discourse_analysis_final_layers/bra_dist_proposed_rr.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

### Dams
Data from Agência Nacional de Energia Elétrica:  
* Cachoeira dos Patos: 5d54m59sS 55d45m36sW  
* Jardim de Ouro:  6d15m49sS 55d45m53sW  
* Jamanxim: 5d38m48sS 55d52m38sW
```{r}
### Dam vectors
dam_names <- c("Cachoeira dos Patos", "Jardim de Ouro", "Jamanxim")
dam_coords <- c("5d54m59r S", "55d45m36r W", "6d15m49r S", "55d45m53r W",
                "5d38m48r S", "55d52m38r W")

### Convert dam_coords to DMS
dam_coords_dd <- as.numeric(char2dms(from = dam_coords, chd = "d", 
                                     chm = "m", chs = "r"))

### Make sf for each dam
cdp_sf <- st_point()

### Make vectors for df
lat_dams <- c(dam_coords_dd[1], dam_coords_dd[3], dam_coords_dd[5])
lon_dams <- c(dam_coords_dd[2], dam_coords_dd[4], dam_coords_dd[6])

### Make df
dams <- data.frame(cbind(dam_names, lat_dams, lon_dams))
dams$lat_dams <- as.numeric(as.character(dams$lat_dams))
dams$lon_dams <- as.numeric(as.character(dams$lon_dams))

### Convert to sf
dams_sf <- st_as_sf(x = dams, 
                    coords = c("lat_dams", "lon_dams"),
                    crs = 102033)

dam_names <- c("Cachoeira dos Patos", "Jardim de Ouro", "Jamanxim")

### CDP
cdp_sf <- data.frame(place = "Cachoeira dos Patos", 
       lat = dam_coords_dd[1], lon = dam_coords_dd[2])
cdp_sf <- st_as_sf(x = cdp_sf, coords = c("lon", "lat"), crs = 102033)


# ### Convert crs
# st_crs(dams_sf) <- 102033

### Write out to inspect
st_write(cdp_sf, "D:/dinamica/brazil_dinamica_data/proposed_infrastr/cdp_dam.shp")
```

## Head of cattle
Municipality-level data from 2017 Censo Agropecuario (https://censos.ibge.gov.br/agro/2017/templates/censo_agro/resultadosagro/pecuaria.html?localidade=15&tema=75652)
```{r}
### Open data
cattle <- read_csv("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/brazil/cattle.csv")

### Merge cattle with municipio geometries
cattle <- merge(cattle, braz, 
                by = "municipio",
                all.x = TRUE)
st_geometry(cattle) <- cattle$geometry

### Calculate municipio area (m2)
cattle$municipio_area_m2 <- st_area(cattle)

### Convert to numeric
cattle$municipio_area_m2 <- as.numeric(cattle$municipio_area_m2)

### Convert to municipality in km2
cattle$municipio_area_km2 <- cattle$municipio_area_m2/1000000

### Calculate cattle per km2
cattle <- cattle %>%
  mutate(cattle_km2 = cattle_head/municipio_area_km2)

### Drop excess columns
cattle <- cattle %>%
  dplyr::select(., municipio, cattle_km2, geometry) %>%
  st_write("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/brazil/cattle.shp")

### Convert to raster in gdal
### gdal_rasterize -a cattle_km2 -tr 30 30 cattle.shp cattle.tiff

### Open raster
cattle_rast <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/brazil/cattle.tiff")

### Resample to match LUC raster (bilinear)
cattle_resample <- raster::resample(cattle_rast, 
                                    jm_2008, "bilinear")

### Save output raster to folder on ext hard drive
writeRaster(cattle_resample,
            filename = "D:/dinamica/brazil_dinamica_data/discourse_analysis_final_layers/bra_cattle.tiff",
            format = "GTiff",
            overwrite = TRUE)

```

## Field research
Locations of field research sites from published lit in Web of Science (searched "Jamanxim," pulled out lat/long of research sites, made kmz in Google Earth, then converted to shp in ArcGIS)
```{r}
### Open shp and reproject
f_r <- st_read("D:/dinamica/brazil_dinamica_data/field_research_sites/jaman_research.shp") %>%
  st_transform(., 102033) 

### Add column for field research site ID
f_r <- f_r %>%
  mutate(., fr_site = 1:nrow(f_r)) %>%
  dplyr::select(., fr_site, geometry)

### Intersect field research sites and jaman buff
f_r <- st_intersection(f_r, jam_big)

### Write out so can calculate distance raster in Arc
st_write(f_r, 
         "D:/dinamica/brazil_dinamica_data/field_research_sites/jam_field_research.shp")

### Make distance raster in ArcGIS. Set max dist to 164400, export as tif: jam_dist_fr.tif

### Open tif
fr_dist <- raster("D:/dinamica/brazil_dinamica_data/field_research_sites/jam_dist_fr.tif")

### Resample to match Jaman raster
fr_resample <- raster::resample(fr_dist, jm_2008, "bilinear")

### Save output raster to folder on ext hard drive
writeRaster(fr_resample,
            filename = "D:/dinamica/brazil_dinamica_data/discourse_analysis_final_layers/jam_dist_fr.tif",
            format = "GTiff",
            overwrite = TRUE)
```

