---
title: "case_study_sites"
author: "Katherine Siegel"
date: "May 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(sf)
library(wdpar)
```

## Jamanxim
```{r}
### Get Brazil data
braz_raw <- wdpa_fetch("Brazil")

### Subset to Jamanxim NF
jaman <- subset(braz_raw, WDPA_PID == "351814")

### Look at crs
jaman ### file in EPSG 4326

### Transform to equal area projection (ESRI South America Equidistant Conic)
jaman <- st_transform(jaman, crs = 102033)

### Make 10km and 20km buffers
buff_10 <- st_buffer(jaman, 10000)
buff_20 <- st_buffer(jaman, 20000)

### Drop overlap between buff_20 and buff_10 (want buff_20 as ring)
buff_20_diff <- st_difference(buff_20, st_union(buff_10))

### Drop overlap between buff_10 and jaman (want buff_10 as ring)
buff_10_diff <- st_difference(buff_10, st_union(jaman))

### Add column to each file with what it is
buff_10_diff <- buff_10_diff %>%
  mutate(NAME = "ten_k_buff",
         category = as.integer(10)) %>%
  dplyr::select(., NAME, category, geometry)
buff_20_diff <- buff_20_diff %>%
  mutate(NAME = "twenty_k_buff",
         category = as.integer(20)) %>%
  dplyr::select(., NAME, category, geometry)
jaman <- jaman %>%
  mutate(category = as.integer(1)) %>%
  dplyr::select(., NAME, category, geometry)

### Combine into single file
jaman_buffers <- rbind(jaman, buff_10_diff,
                       buff_20_diff)

jaman_buffers$category <- as.factor(jaman_buffers$category)

### Write feature
st_write(jaman_buffers, 
         "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/brazil/jaman_w_buffer.shp")
```
Convert to raster in gdal
gdal_rasterize -a category -tr 30 30 jaman_w_buffer.shp jaman_w_buffer.tiff

## Amboro-Carrasco
```{r}
### Open Amboro and Carrasco shp (from protectedplanet)
amb <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/AmbCar/WDPA_Aug2019_protected_area_9779-shapefile-polygons.shp") %>%
  mutate(management = "amboro",
         management_type = "np",
         category = "1")
amb_imna <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/AmbCar/WDPA_Feb2020_protected_area_303887-shapefile-polygons.shp") %>%
  mutate(management = "amboro_imna",
         management_type = "imna",
         category = "2")
car <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/AmbCar/WDPA_Aug2019_protected_area_20037-shapefile-polygons.shp") %>%
  mutate(management = "carrasco",
         management_type = "np",
         category = "3")

### Combine to single sf
ambcar <- rbind(amb, amb_imna, car)

### Transform to equal area projection (ESRI South America Equidistant Conic)
ambcar <- st_transform(ambcar, crs = 102033)

### Make unioned version for buffers
ambcar_union <- st_union(ambcar)

### Make 10km and 20km buffers
buff_10 <- st_buffer(ambcar_union, 10000)
buff_20 <- st_buffer(ambcar_union, 20000)

### Drop overlap between buff_20 and buff_10 (want buff_20 as ring)
buff_20_diff <- st_difference(buff_20, st_union(buff_10))

### Drop overlap between buff_10 and ambcar (want buff_10 as ring)
buff_10_diff <- st_difference(buff_10, st_union(ambcar_union))

### Make dfs for buffer sfs
buff_10_df <- data.frame(NAME = "ten_k_buff",
                         category = as.integer(10))
buff_20_df <- data.frame(NAME = "twenty_k_buff",
                         category = as.integer(20))

### Add column to buffer files with what they are
buff_10_diff <- merge(buff_10_diff, buff_10_df)
buff_20_diff <- merge(buff_20_diff, buff_20_df)

### Combine buffers and reorder columns
buffer_sf <- rbind(buff_10_diff,
                   buff_20_diff)
buffer_sf <- buffer_sf %>%
  dplyr::select(., NAME, category, geometry)
st_geometry(buffer_sf) <- buffer_sf$geometry

### Drop excess cols for ambcar
ambcar <- ambcar %>%
  dplyr::select(., NAME, category, geometry)

### Combine into single file
ambcar_buffers <- rbind(ambcar, buffer_sf)

# ### Drop excess columns
# ambcar_buffers <- dplyr::select(ambcar_buffers,
#                                 NAME = NAME, 
#                                 category = category,
#                                 geometry = geometry)

### Convert character to factor
ambcar_buffers$category <- as.factor(ambcar_buffers$category)

### Write feature
st_write(ambcar_buffers, 
         "D:/dinamica/processed_layers/ambcar_proj_buffers.shp")
st_write(ambcar_buffers,
         "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/ambcar_w_buffer.shp")
```

Convert to raster in gdal
gdal_rasterize -a category -tr 30 30 ambcar_w_buffers.shp ambcar_w_buffers.tiff 
(copy output to "final" and "bolivia_simple/data")

## old misc
ogr2ogr -clipsrc -skipfailures braz_northern_states.shp braz_northern_rds.shp braz_roads_projected.shp
