---
title: "case_study_sites"
author: "Katherine Siegel"
date: "May 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(sf)
library(wdpar)
```

## Jamanxim
```{r}
### Get Brazil data
braz_raw <- wdpa_fetch("Brazil")

### Subset to Jamanxim NF
jaman <- subset(braz_raw, WDPA_PID == "351814")

### Look at crs
jaman ### file in EPSG 4326

### Transform to equal area projection (ESRI South America Equidistant Conic)
jaman <- st_transform(jaman, crs = 102033)

### Make 10km and 20km buffers
buff_10 <- st_buffer(jaman, 10000)
buff_20 <- st_buffer(jaman, 20000)

### Drop overlap between buff_20 and buff_10 (want buff_20 as ring)
buff_20_diff <- st_difference(buff_20, st_union(buff_10))

### Drop overlap between buff_10 and jaman (want buff_10 as ring)
buff_10_diff <- st_difference(buff_10, st_union(jaman))

### Add column to each file with what it is
jaman$category <- as.integer(1)
buff_10_diff$category <- as.integer(10)
buff_20_diff$category <- as.integer(20)

as.factor("protected")
buff_10_diff$category <- as.factor("buffer_10k")
buff_20_diff$category <- as.factor("buffer_20k")

### Combine into single file
jaman_buffers <- rbind(jaman, buff_10_diff, buff_20_diff)

### Write feature
st_write(jaman_buffers, 
         "~/Documents/SESYNC/dinamica/processed_layers/jaman_proj_buffers.shp")
```
Convert to raster in gdal
gdal_rasterize -a category -tr 30 30 jaman_proj_buffers.shp jaman_proj_buffers.tiff

## Amboro-Carrasco
```{r}
### Open Amboro and Carrasco shp (from protectedplanet)
amb <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/AmbCar/WDPA_Aug2019_protected_area_9779-shapefile-polygons.shp")
car <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/AmbCar/WDPA_Aug2019_protected_area_20037-shapefile-polygons.shp")

### Union to single sf
ambcar <- st_union(amb, car)

### Transform to equal area projection (ESRI South America Equidistant Conic)
ambcar <- st_transform(ambcar, crs = 102033)

### Make 10km and 20km buffers
buff_10 <- st_buffer(ambcar, 10000)
buff_20 <- st_buffer(ambcar, 20000)

### Drop overlap between buff_20 and buff_10 (want buff_20 as ring)
buff_20_diff <- st_difference(buff_20, st_union(buff_10))

### Drop overlap between buff_10 and jaman (want buff_10 as ring)
buff_10_diff <- st_difference(buff_10, st_union(ambcar))

### Add column to each file with what it is
ambcar$category <- as.integer(1)
buff_10_diff$category <- as.integer(10)
buff_20_diff$category <- as.integer(20)

### Combine into single file
ambcar_buffers <- rbind(ambcar, buff_10_diff,
                        buff_20_diff)

### Drop excess columns
ambcar_buffers <- dplyr::select(ambcar_buffers,
                                NAME = NAME, 
                                category = category,
                                geometry = geometry)

### Write feature
st_write(ambcar_buffers, 
         "D:/dinamica/processed_layers/ambcar_proj_buffers.shp")
```

Convert to raster in gdal
gdal_rasterize -a category -tr 30 30 ambcar_proj_buffers.shp ambcar_proj_buffers.tiff 
(copy output to "final" and "bolivia_simple/data")

## old misc
ogr2ogr -clipsrc -skipfailures braz_northern_states.shp braz_northern_rds.shp braz_roads_projected.shp
