---
title: "dinamica_comparison"
author: "Katherine Siegel"
date: "February 19, 2020"
output: html_document
---

## Description
Compare transitions from actual 2018 map vs DINAMICA's simulation.

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
library(lwgeom)
library(sp)
library(lubridate)
library(rgdal)

### File paths
#### DINAMICA maps
bol_din <- "D:/dinamica/bolivia_simple/5_run_lucc/"
bra_din <- "D:/dinamica/brazil_simple/5_run_lucc/"

### Remote sensing maps
bol_dat <- "D:/dinamica/bolivia_simple/data/"
bra_dat <- "D:/dinamica/brazil_simple/data/"

### Save visuals here
vis_save <- "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/visuals_feb/"
```

## Brazil
Open .ers files in ArcMap and export as .tif, then reproject using gdal
probabilities10_bra.tif, landscape10_bra.tif [_rpj for reprojected files]

gdalwarp -t_srs EPSG:102033 -r near landscape10_bra.tif landscape10_bra_rpj.tif

### Landscape
#### Compare forested pts
```{r}
### Open observed 2018 landscape
obs_bra <- raster(paste0(bra_dat,
                         "classi_bra_dry_2018_102033.tif"))

### Open simulated 2018 landscape
sim_bra <- raster(paste0(bra_din,
                         "landscape10_bra_rpj.tif"))

### Get number of forest points in each
obs_bra_count <- data.frame(freq(obs_bra))
sim_bra_count <- data.frame(freq(sim_bra))  

### Add col for source
obs_bra_count <- obs_bra_count %>%
  mutate(Source = "Observed map")
sim_bra_count <- sim_bra_count %>%
  mutate(Source = "Simulated map") 

### Combine
bra_counts <- rbind(obs_bra_count, sim_bra_count)

### Drop 0 and NA
bra_counts <- bra_counts %>%
  filter(., value > 0)

### Column for land cover class
bra_counts <- bra_counts %>%
  mutate(landcover = ifelse(value == "1",
                            "Ag",
                            ifelse(value == "2",
                                   "Forest",
                                   ifelse(value == "3",
                                          "Bare",
                                          ifelse(value == "4",
                                                 "Urban",
                                                 ifelse(value == "5", "Wetland", "Water"))))))

### Divide count by 1,000,000
bra_counts <- bra_counts %>%
  mutate(count_mil = count/1000000)

### Visualize
bra_counts %>%
  ggplot(aes(x = landcover, y = count_mil, fill = Source)) +
  geom_bar(stat = "identity", position=position_dodge()) +
  xlab("Land cover type") + ylab("Millions of pixels") +
  theme_bw() +
  theme(text = element_text(size = 15))
ggsave(paste0(vis_save, "bra_count_comparison.png"))

### Summarize bra counts
bra_counts <- bra_counts %>%
  mutate(total_pixels = 30302960,
         percent_pixels = count/total_pixels*100)
```

#### Compare forest to ag transitions
```{r}
### Open 2008 map
bra_2008 <- raster(paste0(bra_dat,
                          "classi_bra_dry_2008_102033.tif"))

### Reclassify rasters so ag = 1, forest = 10, all others = 0
### Reclassification matrix
reclass_df <- c(0, 0.9, NA,   ## change NoData to NA
                0.9, 1.1, 1,  ## ag = 1
                1.9, 2.1, 10, ## forest = 2
                2.9, 8, 0)    ## all other classes = 0
reclass_m <- matrix(reclass_df,
                ncol = 3,
                byrow = TRUE)

### Reclassify all maps
bra_2008_recl <- reclassify(bra_2008, reclass_m)
bra_2018_obs <- reclassify(obs_bra, reclass_m)
bra_2018_sim <- reclassify(sim_bra, reclass_m)

### Get transitions in observed maps
obs_trans <- bra_2018_obs - bra_2008_recl
obs_trans_count <- data.frame(freq(obs_trans))
obs_trans_count <- obs_trans_count %>%
  mutate(Source = "Observed map") 

### Get transitions in simulated map
sim_trans <- bra_2018_sim - bra_2008_recl
sim_trans_count <- data.frame(freq(sim_trans))
sim_trans_count <- sim_trans_count %>%
  mutate(Source = "Simulated map") 

### Combine
transition_counts <- rbind(obs_trans_count,
                           sim_trans_count)

### Add column for transition type
transition_counts <- transition_counts %>%
  mutate(Transition = ifelse(value == "0",
                             "No change",
                             ifelse(value == "-10",
                                    "Forest -> Other",
                                    ifelse(value == "-9",
                                           "Forest -> Ag",
                                           ifelse(value == "-1",
                                                  "Ag -> Other",
                                                  ifelse(value == "1", "Other -> Ag", ifelse(value == "9", "Ag -> Forest", "Other -> Forest")))))))

### Write out tifs with transitions
writeRaster(obs_trans, 
            filename = paste0(vis_save, 
                              "bra_obs_transitions.tif"),
            format = "GTiff")
writeRaster(sim_trans, 
            filename = paste0(vis_save, 
                              "bra_sim_transitions.tif"),
            format = "GTiff")
```

##### Compare btw methods
```{r}
### Reclassify transition maps: want 10 = forest to ag transition (-9 in previous map), all other transitions = 1 in sim and 2 in obs, no change = 5 in both

### Reclassification df for obs
reclass_df_obs <- c(-10.1, -9.9, 2, # Forest -> Other = 2
                    -9.5, -8.9, 10,   # Forest -> Ag = 10
                    -2, -0.9, 2,      # Ag -> Other = 2
                    -0.5, 0.5, 5,     # No Change = 5
                    0.6, 11, 2)       # All other changes = 2 ### Convert to matrix                
reclass_m_obs <- matrix(reclass_df_obs,
                      ncol = 3,
                      byrow = TRUE)

### Reclassification df for sim
reclass_df_sim <- c(-9.5, -8.9, 10,   # Forest -> Ag = 10
                    -0.5, 0.5, 6)     # No Change = 6

 ### Convert to matrix                
reclass_m_sim <- matrix(reclass_df_sim,
                      ncol = 3,
                      byrow = TRUE)

### Reclassify rasters
obs_trans_recl <- reclassify(obs_trans, reclass_m_obs)
sim_trans_recl <- reclassify(sim_trans, reclass_m_sim)

### Subtract observed from simulated
diff_trans <- sim_trans_recl + obs_trans_recl

### Get counts
diff_trans_count <- data.frame(freq(diff_trans))

### Percent of pixels
diff_trans_count <- diff_trans_count %>%
  mutate(total_pixels = 61272100,
         percent_pix = count/total_pixels*100)

### If value = __, difference is: 
### 8: Sim = no change, Obs = other change
### 11: both = no change
### 12: Sim = forest to ag, Obs = other change
### 15: Sim = forest to ag, Obs = no change
### 16: Sim = no change, Obs = forest to ag
### 20: both = forest to ag

### Write out raster
writeRaster(diff_trans, 
            filename = paste0(vis_save, 
                              "bra_transiti_diffs.tif"),
            format = "GTiff")
```


## Bolivia
Open .ers files in ArcMap and export as .tif, then reproject using gdal
probabilities10_bol.tif, landscape10_bol.tif

### Landscape
#### Compare forested pts
```{r}
### Open observed 2018 landscape
obs_bol <- raster(paste0(bol_dat,
                         "classi_bol_dry_2018_102033.tif"))

### Open simulated 2018 landscape
sim_bol <- raster(paste0(bol_din,
                         "landscape10_reproj.tif"))

### Get number of forest points in each
obs_bol_count <- data.frame(freq(obs_bol))
sim_bol_count <- data.frame(freq(sim_bol))  

### Add col for source
obs_bol_count <- obs_bol_count %>%
  mutate(Source = "Observed map")
sim_bol_count <- sim_bol_count %>%
  mutate(Source = "Simulated map") 

### Combine
bol_counts <- rbind(obs_bol_count, sim_bol_count)

### Drop 0 and NA
bol_counts <- bol_counts %>%
  filter(., value > 0)

### Column for land cover class
bol_counts <- bol_counts %>%
  mutate(landcover = ifelse(value == "1",
                            "Ag",
                            ifelse(value == "2",
                                   "Forest",
                                   ifelse(value == "3",
                                          "Bare",
                                          ifelse(value == "4",
                                                 "Urban",
                                                 ifelse(value == "5", "Wetland", ifelse(value == "6", "Desert", "Water")))))))
                                                        

### Divide count by 1,000,000
bol_counts <- bol_counts %>%
  mutate(count_mil = count/1000000)

### Visualize
bol_counts %>%
  ggplot(aes(x = landcover, y = count_mil, fill = Source)) +
  geom_bar(stat = "identity", position=position_dodge()) +
  xlab("Land cover type") + ylab("Millions of pixels") +
  theme_bw() +
  theme(text = element_text(size = 15))
ggsave(paste0(vis_save, "bol_count_comparison.png"))

### Summarize bol counts
bol_counts <- bol_counts %>%
  mutate(total_pixels = 34128657,
         percent_pixels = count/total_pixels*100)
```

#### Compare forest to ag transitions
```{r}
### Open 2008 map
bol_2008 <- raster(paste0(bol_dat,
                          "classi_bol_dry_2008_102033.tif"))

### Reclassify rasters so ag = 1, forest = 10, all others = 0
### Reclassification matrix
reclass_df <- c(0, 0.9, NA,   ## change NoData to NA
                0.9, 1.1, 1,  ## ag = 1
                1.9, 2.1, 10, ## forest = 2
                2.9, 8, 0)    ## all other classes = 0
reclass_m <- matrix(reclass_df,
                ncol = 3,
                byrow = TRUE)

### Reclassify all maps
bol_2008_recl <- reclassify(bol_2008, reclass_m)
bol_2018_obs <- reclassify(obs_bol, reclass_m)
bol_2018_sim <- reclassify(sim_bol, reclass_m)

### Get transitions in observed maps
obs_trans_bol <- bol_2018_obs - bol_2008_recl
obs_trans_count_bol <- data.frame(freq(obs_trans_bol))
obs_trans_count_bol <- obs_trans_count_bol %>%
  mutate(Source = "Observed map") 

### Get transitions in simulated map
sim_trans_bol <- bol_2018_sim - bol_2008_recl
sim_trans_count_bol <- data.frame(freq(sim_trans_bol))
sim_trans_count_bol <- sim_trans_count_bol %>%
  mutate(Source = "Simulated map") 

### Combine
transition_counts_bol <- rbind(obs_trans_count_bol,
                           sim_trans_count_bol)

### Add column for transition type
transition_counts_bol <- transition_counts_bol %>%
  mutate(Transition = ifelse(value == "0",
                             "No change",
                             ifelse(value == "-10",
                                    "Forest -> Other",
                                    ifelse(value == "-9",
                                           "Forest -> Ag",
                                           ifelse(value == "-1",
                                                  "Ag -> Other",
                                                  ifelse(value == "1", "Other -> Ag", ifelse(value == "9", "Ag -> Forest", "Other -> Forest")))))))

### Write out tifs with transitions
writeRaster(obs_trans_bol, 
            filename = paste0(vis_save, 
                              "bol_obs_transitions.tif"),
            format = "GTiff")
writeRaster(sim_trans_bol, 
            filename = paste0(vis_save, 
                              "bol_sim_transitions.tif"),
            format = "GTiff")
```

##### Compare btw methods
```{r}
### Reclassify transition maps: want 10 = forest to ag transition (-9 in previous map), all other transitions = 1 in sim and 2 in obs, no change = 5 in both

### Reclassification df for obs
reclass_df_obs <- c(-10.1, -9.9, 2, # Forest -> Other = 2
                    -9.5, -8.9, 10,   # Forest -> Ag = 10
                    -2, -0.9, 2,      # Ag -> Other = 2
                    -0.5, 0.5, 5,     # No Change = 5
                    0.6, 11, 2)       # All other changes = 2 ### Convert to matrix                
reclass_m_obs <- matrix(reclass_df_obs,
                      ncol = 3,
                      byrow = TRUE)

### Reclassification df for sim
reclass_df_sim <- c(-9.5, -8.9, 10,   # Forest -> Ag = 10
                    -0.5, 0.5, 6)     # No Change = 6

 ### Convert to matrix                
reclass_m_sim <- matrix(reclass_df_sim,
                      ncol = 3,
                      byrow = TRUE)

### Reclassify rasters
obs_trans_bol_recl <- reclassify(obs_trans_bol, 
                                 reclass_m_obs)
sim_trans_bol_recl <- reclassify(sim_trans_bol,
                                 reclass_m_sim)

### Subtract observed from simulated
diff_trans_bol <- sim_trans_bol_recl + obs_trans_bol_recl

### Get counts
diff_trans_count_bol <- data.frame(freq(diff_trans_bol))

### Percent of pixels
diff_trans_count_bol <- diff_trans_count_bol %>%
  mutate(total_pixels = 34128657,
         percent_pix = count/total_pixels*100)

### If value = __, difference is: 
### 8: Sim = no change, Obs = other change
### 11: both = no change
### 12: Sim = forest to ag, Obs = other change
### 15: Sim = forest to ag, Obs = no change
### 16: Sim = no change, Obs = forest to ag
### 20: both = forest to ag

### Write out raster
writeRaster(diff_trans_bol, 
            filename = paste0(vis_save, 
                              "bol_transiti_diffs.tif"),
            format = "GTiff")
```