---
title: "dinamica_prep"
author: "Katherine Siegel"
date: "April 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
library(stars)
```

## Amboro-Carrasco

### Population density
```{r}
### Open shp of buffer
ambcar <- st_read("~/Documents/SESYNC/dinamica/case_study_shp/AmbCar/AmbCarBuf.shp")

### Transform to equal area projection (ESRI South America Equidistant Conic)
ambcar_pr <- st_transform(ambcar, crs = 102033)

### Open shp of municipios
municip <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/pop_dens/municipios_339_pob2012.shp") %>% 
  st_transform(., crs = 102033)
st_write(municip, 
         "~/Documents/SESYNC/dinamica/bolivia_dinamica_data/pop_dens/municipios_339_pob2012_projected.shp")

### intersect pop density and PA polygon
ambcar_pd <- st_intersection(ambcar_pr, municip)
st_write(ambcar_pd, 
         "~/Documents/SESYNC/dinamica/processed_layers/bol_popdens.shp")
```
Converted this to raster using gdal in gitbash: 
gdal_rasterize -a densidad12 -tr 30 30 bol_popdens.shp bol_popdens.tiff

Made raster of population density in ArcMap (Polygon to Raster): pd_2012 (cell size = 30)
```{r}
bolpd <- raster("~/Documents/SESYNC/dinamica/bol_pd.tif")
```

### Rivers
#### Rios principales
Convert crs
```{r}
rios_princ <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_2002/rios_principales.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
rios_princ <- rios_princ %>%
  mutate(label = 1)

### Save projected version
st_write(rios_princ, "~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_2002/rios_principales_projected.shp")
```
Converted this to raster using gdal in gitbash: 
gdal_rasterize -a label -a_nodata 0 -tr 30 30 filename.shp filename.tiff

#### other code to convert to raster
```{r}
### Convert to raster
presence.absence.raster <- function(mask.raster, 
                                    env.data,
                                    raster.label = "") {
  require(raster)
  
  # set the background cells in the raster to 0
  mask.raster[!is.na(mask.raster)] <- 0
  
  # set the cells that contain rivers to 1
  env.raster <- rasterize(env.data, mask.raster, field = 1)
  env.raster <- merge(env.raster, mask.raster)
  
  #label the raster
  names(env.raster) <- raster.label
  return(env.raster)
}
```

#### Rios menores
Convert crs
```{r}
rios_men <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_menores/rios_menores.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
rios_men <- rios_men %>%
  mutate(label = 1)

### Save projected version
st_write(rios_men, "~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_menores/rios_menores_projected.shp")
```

### Roads
```{r}
### Open and reproject
boli_rds <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/roads_diva_gis/BOL_roads.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
boli_rds <- boli_rds %>%
  mutate(label = 1)

### Save projected version
st_write(boli_rds, "~/Documents/SESYNC/dinamica/processed_layers/boli_roads_projected.shp")
```

### Poverty rate
```{r}
### Open and reproject
boli_pobr <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/pobreza/nbi_vam_2012.shp") %>%
  st_transform(., crs = 102033) %>%
st_write(boli_pobr, 
         "~/Documents/SESYNC/dinamica/processed_layers/boli_pobr_projected.shp")
```

## Jamanxim
### Roads
```{r}
### Open and reproject
braz_rds <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/BRA_roads_divagis.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
braz_rds <- braz_rds %>%
  mutate(label = 1)

# ### Save projected version
# st_write(braz_rds, "~/Documents/SESYNC/dinamica/processed_layers/braz_roads_projected.shp")

### Crop to just include Para
braz <- getData('GADM', country = "Brazil", level = 1) %>%
  st_as_sf() %>%
  subset(., GID_1 == "BRA.14_1") %>%
  st_transform(., crs = 102033)
st_write(braz, 
         "~/Documents/SESYNC/dinamica/processed_layers/braz_para_bound.shp")
```

### Pop density
```{r}
### Open file
braz_pd <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/popdens/para_pop_density.shp") %>%
  st_transform(., crs = 102033)

### Save output
st_write(braz_pd, "~/Documents/SESYNC/dinamica/processed_layers/braz_popdens_projected.shp")
```

