---
title: "bolivia_dinamica_prep_2"
author: "Katherine Siegel"
date: "October 9, 2019"
output: html_document
---

## Description
Need to re-do clipping of Bolivia files to reflect new shapefile (Eva noticed error in original shp 9/27/2019). The new shapefile is larger than the old one, so will need to go back to larger data layers and clip them, rather than clipping the ones I already processed.

Store these files in new folder in external hard drive: bolivia_dinamica_data_9_27

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
# library(stars)
```

## New case study polygon
```{r}
### Open shp of new buffer
ambcar <- st_read("D:/dinamica/bolivia_dinamica_data/AmbCar_Buffer_9_27/Bol_buffer.shp") %>%
  st_transform(., crs = 102033)

### Save reprojected buffer
st_write(ambcar,
         "D:/dinamica/bolivia_dinamica_data_9_27/bol_buff_pr.shp")

### New case study raster
### Reprojected to 102033 in QGIS
ambcar_rast <- raster("D:/dinamica/bolivia_dinamica_data_9_27/bol_2018_class.tif")
```

## New layers
### Population density
```{r}
### Open shp of municipios (reprojected in dinamica_prep.Rmd)
municip <- st_read("D:/dinamica/bolivia_dinamica_data/pop_dens/municipios_339_pob2012_projected.shp")

### Intersect pop density and PA polygon
ambcar_pd <- st_intersection(ambcar, municip)
st_write(ambcar_pd,
         "D:/dinamica/bolivia_dinamica_data_9_27/bol_popdens.shp")

### Converted this to raster using gdal in gitbash: 
# gdal_rasterize -a densidad12 -tr 30 30 bol_popdens.shp bol_popdens.tiff

### Open raster to resample to match LUC map
ambcar_pd_r <- raster("D:/dinamica/bolivia_dinamica_data_9_27/bol_popdens.tiff")

### Resample
bpd_resample <- raster::resample(ambcar_pd_r, 
                                 ambcar_rast, 
                                 "bilinear")

### Save resampled output
writeRaster(bpd_resample,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/bol_popdens_927.tiff",
            format = "GTiff")
```

### Rivers
Use rios menores file processed in dinamica_prep.Rmd
```{r}
### Make buffer around ambcar shp to use to clip rios menores shp
ambcar_buff <- st_buffer(ambcar, dist = 30000)

### Open rios menores shp
rios <- st_read("D:/dinamica/bolivia_dinamica_data/rios/rios_menores/rios_menores_projected.shp")

### Drop rivers outside buffered shp
rios_ambcar <- st_intersection(rios, ambcar_buff)

### Write out rios_ambcar so can calculate distance raster in Arc
st_write(rios_ambcar, 
         "D:/dinamica/bolivia_dinamica_data_9_27/ambcar_rios.shp")

### Calculate distance to rivers in Arc (set max distance to 12600 meters to capture variation)
### Then export as tif: riv_dist.tif

### Open tif
riv_dist <- raster("D:/dinamica/bolivia_dinamica_data_9_27/riv_dist.tif")

### Resample to match AC raster
ambcar_rios_resample <- raster::resample(riv_dist, 
                                         ambcar_rast,
                                         "bilinear")

### Save output raster
writeRaster(ambcar_rios_resample,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/bol_dist_rios_menores_927.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

### Roads
Use OSM layer from dinamica_prep.Rmd
```{r}
### Open and reproject
boli_rds <- st_read("D:/dinamica/bolivia_dinamica_data/roads_diva_gis/BOL_roads.shp") %>%
  st_transform(., crs = 102033)

### Make larger intersection buffer for roads (fewer roads than rivers)
ambcar_buff_large <- st_buffer(ambcar, dist = 50000)

### Intersect roads and ambcar buff
ambcar_rds <- st_intersection(boli_rds, 
                              ambcar_buff_large)

### Write out rios_ambcar so can calculate distance raster in Arc
st_write(ambcar_rds, 
         "D:/dinamica/bolivia_dinamica_data_9_27/ambcar_rds.shp")

### Calculate distance to rivers in Arc (set max distance to 50000 meters to capture variation)
### Then export as tif: rd_dist.tif

### Open tif
rd_dist <- raster("D:/dinamica/bolivia_dinamica_data_9_27/rd_dist.tif")

### Resample to match AC raster
ambcar_rds_resample <- raster::resample(rd_dist, 
                                         ambcar_rast,
                                         "bilinear")

### Save output raster
writeRaster(ambcar_rds_resample,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/bol_dist_rds_927.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

### Poverty rate
```{r}
### Open pov rate raster
ambcar_pov <- raster("D:/dinamica/processed_layers/boli_pobr_clip.tif")

### Resample to match ac_2008
ambcar_pov_resample <- raster::resample(ambcar_pov, 
                                         ac_2008, "bilinear")

### Save output raster
writeRaster(ambcar_pov_resample,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/final/bol_pobreza.tiff",
            format = "GTiff")
```



