---
title: "dinamica_prep"
author: "Katherine Siegel"
date: "April 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
library(stars)
```

## Amboro-Carrasco

### Shapefile of Amb-Car
```{r}
### Open shp of buffer
ambcar <- st_read("~/Documents/SESYNC/dinamica/case_study_shp/AmbCar/AmbCarBuf.shp")

### Transform to equal area projection (ESRI South America Equidistant Conic)
ambcar_pr <- st_transform(ambcar, crs = 102033)

### Add column for label
ambcar_pr$label <- 1

### Save ouput
st_write(ambcar_pr, 
         "~/Documents/SESYNC/dinamica/processed_layers/ambcar_proj.shp")
```


### Population density
```{r}
### Open shp of municipios
municip <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/pop_dens/municipios_339_pob2012.shp") %>% 
  st_transform(., crs = 102033)
st_write(municip, 
         "~/Documents/SESYNC/dinamica/bolivia_dinamica_data/pop_dens/municipios_339_pob2012_projected.shp")

### intersect pop density and PA polygon
ambcar_pd <- st_intersection(ambcar_pr, municip)
st_write(ambcar_pd, 
         "~/Documents/SESYNC/dinamica/processed_layers/bol_popdens.shp")
```
Converted this to raster using gdal in gitbash: 
gdal_rasterize -a densidad12 -tr 30 30 bol_popdens.shp bol_popdens.tiff

Made raster of population density in ArcMap (Polygon to Raster): pd_2012 (cell size = 30)
```{r}
# bolpd <- raster("~/Documents/SESYNC/dinamica/bol_pd.tif")
```

#### 8/12
Resample file so it matches extent and resolution of land use/land cover map
```{r}
### Open pop density shp
ambcar_pd <- st_read("~/Documents/SESYNC/dinamica/processed_layers/bol_popdens.shp")

### Open ambcar LUC raster
ac_2008 <- raster("D:/dinamica/bolivia_simple/data/unsuper_bol_2008_dry_102033.tif")

### Get extent
ambcar_ext <- extent(ac_2008)

### Crop pop dens to extent
ambcar_pd <- st_crop(ambcar_pd, xmin = -613219.5, ymin = 1585781,
                     xmax = -332403.2, ymax = 1758667)

### Write output
st_write(ambcar_pd, 
         "~/Documents/SESYNC/dinamica/processed_layers/bol_popdens_cropped.shp")

### Rasterize in gdal:  
### gdal_rasterize -a densidad12 -tr 28.21707 28.21707 bol_popdens_cropped.shp bol_popdens_test.tiff

### Open gdal raster output
bpd_test <- raster("~/Documents/SESYNC/dinamica/processed_layers/bol_popdens_test.tiff")

### Resample to match ac_2008
bpd_resample <- raster::resample(bpd_test, ac_2008, "bilinear")

### Save output raster
writeRaster(bpd_resample,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/final/bol_popdens.tiff",
            format = "GTiff")
```

### Rivers
#### Rios principales
Convert crs
```{r}
rios_princ <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_2002/rios_principales.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
rios_princ <- rios_princ %>%
  mutate(label = 1)

### Save projected version
st_write(rios_princ, "~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_2002/rios_principales_projected.shp")
```

#### Rios menores
Convert crs
```{r}
rios_men <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_menores/rios_menores.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
rios_men <- rios_men %>%
  mutate(label = 1)

### Save projected version
st_write(rios_men, "~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_menores/rios_menores_projected.shp")
```

Converted this to raster using gdal in gitbash: 
gdal_rasterize -a label -a_nodata 0 -tr 30 30 filename.shp filename.tiff

#### 8/12
```{r}
### Open rios raster
ambcar_rios <- raster("~/Documents/SESYNC/dinamica/processed_layers/bol_dist_rios_menores.tif")

### Resample to match ac_2008
ambcar_rios_resample <- raster::resample(ambcar_rios, 
                                         ac_2008, "bilinear")

### Save output raster
writeRaster(ambcar_rios_resample,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/final/bol_dist_rios_menores.tiff",
            format = "GTiff")
```

### Roads (DIVA GIS)
```{r}
### Open and reproject
boli_rds <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/roads_diva_gis/BOL_roads.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
boli_rds <- boli_rds %>%
  mutate(label = 1)

### Save projected version
st_write(boli_rds, "~/Documents/SESYNC/dinamica/processed_layers/boli_roads_projected.shp")
```

### Roads (OSM)
```{r}
### Open and reproject
boli_osm <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/openstreetmap/ambcar_rds.shp") %>%
  st_transform(., crs = 102033)

### Save projected version
st_write(boli_osm, "~/Documents/SESYNC/dinamica/processed_layers/boli_osm_roads_projected.shp")
```

#### 8/12
```{r}
### Open roads raster
ambcar_rds <- raster("~/Documents/SESYNC/dinamica/processed_layers/bol_osm_dist.tif")

### Resample to match ac_2008
ambcar_rds_resample <- raster::resample(ambcar_rds, 
                                         ac_2008, "bilinear")

### Save output raster
writeRaster(ambcar_rds_resample,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/final/bol_dist_rds.tiff",
            format = "GTiff")
```

### Poverty rate
```{r}
### Open and reproject
boli_pobr <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/pobreza/nbi_vam_2012.shp") %>%
  st_transform(., crs = 102033) %>%
st_write(boli_pobr, 
         "~/Documents/SESYNC/dinamica/processed_layers/boli_pobr_projected.shp")
```

#### 8/12
```{r}
### Open pov rate raster
ambcar_pov <- raster("~/Documents/SESYNC/dinamica/processed_layers/boli_pobr_clip.tif")

### Resample to match ac_2008
ambcar_pov_resample <- raster::resample(ambcar_pov, 
                                         ac_2008, "bilinear")

### Save output raster
writeRaster(ambcar_pov_resample,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/final/bol_pobreza.tiff",
            format = "GTiff")
```

### Crop suitability
#### 8/12
```{r}
### Open crop suit raster
ambcar_cs <- raster("~/Documents/SESYNC/dinamica/processed_layers/crop_suit_ambcar.tif")

### Resample to match ac_2008
ambcar_cs_resample <- raster::resample(ambcar_cs, 
                                         ac_2008, "bilinear")

### Save output raster
writeRaster(ambcar_cs_resample,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/final/bol_cropsuit.tiff",
            format = "GTiff")
```

## Jamanxim

### Shapefile of Jamanxim
```{r}
### Open shp of buffer
jambuf <- st_read("~/Documents/SESYNC/dinamica/case_study_shp/JamanBuffer/JamanBuffer.shp")

### Transform to equal area projection (ESRI South America Equidistant Conic)
jambuf_pr <- st_transform(jambuf, crs = 102033)

### Save ouput
st_write(jambuf_pr, 
         "~/Documents/SESYNC/dinamica/processed_layers/jaman_proj.shp")
```

### Roads (DIVA GIS)
```{r}
### Open and reproject
braz_rds <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/BRA_roads_divagis.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
braz_rds <- braz_rds %>%
  mutate(label = 1)

# ### Save projected version
# st_write(braz_rds, "~/Documents/SESYNC/dinamica/processed_layers/braz_roads_projected.shp")

### Crop to just include Para
braz <- getData('GADM', country = "Brazil", level = 1) %>%
  st_as_sf() %>%
  subset(., GID_1 == "BRA.14_1") %>%
  st_transform(., crs = 102033)
st_write(braz, 
         "~/Documents/SESYNC/dinamica/processed_layers/braz_para_bound.shp")

### Crop to northern brazilian states
braz <- getData('GADM', country = "Brazil", level = 1) %>%
  st_as_sf() %>%
  subset(., GID_1 == "BRA.14_1" |
           GID_1 == "BRA.4_1" |
           GID_1 == "BRA.12_1" |
           GID_1 == "BRA.22_1") %>%
  st_transform(., crs = 102033)
st_write(braz, 
         "~/Documents/SESYNC/dinamica/processed_layers/braz_northern_states.shp")

### See if there are invalid geoms in roads dataset
any(na.omit(st_is_valid(braz_rds)) == FALSE)

### Intersect
rds_north <- st_intersection(braz_rds, braz)

### Write output roads
st_write(rds_north, 
         "~/Documents/SESYNC/dinamica/processed_layers/braz_rds_northern_states.shp")
```
Cropped in gdal. Made tif of roads in Para using gdal. Then made tif of roads in northern states.

Cropped roads in QGIS/gdal: 
1. made northern states polygon:
braz_rd_northern_bound.shp, then rasterized in gdal: gdal_rasterize -burn 1 -tr 30 30 braz_rd_northern_bound.shp braz_rd_northern_bound.tiff
2. cropped roads to northern states: braz_northern_rds_qgis.shp
3. still too large to rasterize in gdal
4. crop to northern_polygon.shp in gdal ogr2ogr -clipsrc northern_polygon.shp braz_northern_rds.shp braz_northern_rds_qgis.shp
5. still doesn't work.

### Roads (OSM)
```{r}
### Open and reproject
braz_osm <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/openstreetmaps/jaman_rds.shp") %>%
  st_transform(., crs = 102033)

### Save projected version
st_write(braz_osm,
         "~/Documents/SESYNC/dinamica/processed_layers/braz_osm_roads_projected.shp")
```
Clipped to area around Jamanxim in rgdal: braz_osm_roads_projected.shp (epsg: 102033)

##### Open both roads
```{r}
### divagis
dgis <- st_read("~/Documents/SESYNC/dinamica/processed_layers/braz_northern_rds.shp") %>%
  st_transform(., crs = 102033)

### osm
osm <- st_read("~/Documents/SESYNC/dinamica/processed_layers/braz_osm_roads_projected.shp") %>%
  st_transform(., crs = 102033)

### Drop columns
dgis <- dplyr::select(dgis, rast_val = raster_val,
                      geometry = geometry)
osm <- dplyr::select(osm, rast_val = rast_val,
                      geometry = geometry)

### Combine 
all_rd <- rbind(dgis, osm)

### Save 
st_write(all_rd,
         "~/Documents/SESYNC/dinamica/processed_layers/braz_all_raods.shp")
```
gdal_rasterize -a mine -tr 30 30 braz_mines_para_projected.shp braz_mines_para_projected.tiff

### Pop density
```{r}
### Open file
braz_pd <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/popdens/para_pop_density.shp") %>%
  st_transform(., crs = 102033)

### Save output
st_write(braz_pd, "~/Documents/SESYNC/dinamica/processed_layers/braz_popdens_projected.shp")
```
Made tif of pop density in Para using gdal.

### Cities
Map of urban areas over 100k people from 2000
https://ww2.ibge.gov.br/home/geociencias/geografia/mapas_doc1.shtm
```{r}
### Open and reproject
urb <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/areas_urbanizadas_do_brasil_2005_ibge/AreasUrbanizadas_MunicipiosAcima100k_porMunicipio.shp") %>%
  st_transform(., crs = 102033)

### Save output
st_write(urb, "~/Documents/SESYNC/dinamica/processed_layers/braz_urban_projected.shp")
```
Crop urban layer to Para boundaries in gdal
ogr2ogr -clipsrc braz_para_bound.shp braz_para_urb.shp braz_urban_projected.shp

### Mines
```{r}
mines <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/SIGMINE/PA.shp") %>%
  st_transform(., crs = 102033)

### Add column to burn into
mines$mine <- 1

### Save output
st_write(mines,
         "~/Documents/SESYNC/dinamica/processed_layers/braz_mines_para_projected.shp")
```
gdal_rasterize -a mine -tr 30 30 braz_mines_para_projected.shp braz_mines_para_projected.tiff

### Rivers
Data from divagis
```{r}
### Open line files
rio_line <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/BRA_divagis_water/BRA_water_lines_dcw.shp") %>%
  st_transform(., crs = 102033)

rio_line$rio <- 1

### Write out, then crop to Para in gdal
st_write(rio_line,
         "~/Documents/SESYNC/dinamica/processed_layers/bra_rios_proj.shp")
# ### Open area files -- these aren't rivers
# rio_area <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/BRA_divagis_water/BRA_water_areas_dcw.shp") %>%
#   st_transform(., crs = 102033)
```
too slow: ogr2ogr -clipsrc braz_para_bound.shp braz_para_rios.shp bra_rios_proj.shp
Deleted rivers in ArcMap, the converted to raster in gdal

## Global layer
### Crop suitability
```{r}
### Open crop suitability layer
crop_suit <- raster("~/Documents/SESYNC/dinamica/global_dinamica_data/overall_cropsuit_i_1981-2010.tif")

### Too big to project whole file, so need to crop to extent of buffers first 
crs(crop_suit)
```

#### Jamanxim
```{r}
### Open Jamanxim buffered shp
jaman <- st_read("~/Documents/SESYNC/dinamica/case_study_shp/JamanBuffer/JamanBuffer.shp")

### Project Jamanxim to match crs of crop_suit
# target_crs <- crs(crop_suit)
jaman_rpj <- st_transform(jaman, crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

### Make Jamanxim a sp object (raster doesn't work with sf)
jam_sp <- as(jaman_rpj, 'Spatial')

### Crop crops to Jamanxim
crop_jam <- crop(crop_suit, jam_sp)

### Project crop_jam to EPSG 102033
crop_jam_102033 <- projectRaster(crop_jam, 
                                 crs = "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs")

### Disaggregate raster so resolution matches 30x30
crop_jam_disag <- disaggregate(crop_jam_102033,
                               fact = c(30, 31))

### Make empty raster
empty_rast <- raster(ncol = 5550, nrow = 10230,
                     xmn = 380991.3, xmx = 549156.3,
                     ymn = 2670617, ymx = 2978177,
                     crs = "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs",
                     res = c(30, 30))

### Resample to get exact resolution
crop_jam_3030 <- resample(x = crop_jam_disag, 
                          y = empty_rast,
                          method = "bilinear")

### Write output
writeRaster(crop_jam_3030,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/crop_suit_jaman",
            format = "GTiff")
```
proj4string for 102033: +proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs

#### AmbCar
```{r}
### Open Amb buffered shp
ambcar <- st_read("~/Documents/SESYNC/dinamica/case_study_shp/AmbCar/AmbCarBuf.shp")

### Project AmbCar to match crs of crop_suit
ambcar_rpj <- st_transform(ambcar, crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

### Make AmbCar a sp object (raster doesn't work with sf)
ambcar_sp <- as(ambcar_rpj, 'Spatial')

### Crop crops to AmbCar
crop_ac <- crop(crop_suit, ambcar_sp)

### Project crop_jam to EPSG 102033
crop_ac_102033 <- projectRaster(crop_ac, 
                                 crs = "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs")

### Disaggregate raster so resolution matches 30x30
crop_ac_disag <- disaggregate(crop_ac_102033,
                               fact = c(28, 32))

### Make empty raster
empty_rast_ac <- raster(ncol = 9660, nrow = 6048,
                     xmn = -618682.5, xmx = -327157.5,
                     ymn = 1581007, ymx = 1763203,
                     crs = "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs",
                     res = c(30, 30))

######## Couldn't resample because not enough memory!!
### Resample to get exact resolution
crop_ac_3030 <- resample(x = crop_ac_disag, 
                          y = empty_rast_ac,
                          method = "bilinear")

### Write output
writeRaster(crop_ac_3030,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/crop_suit_ambcar",
            format = "GTiff")
```

## Distance to roads
1. rasterize OSM rds in gdal:
gdal_rasterize -a rast_val -tr 30 30 braz_osm_roads_projected.shp braz_osm_rds.tiff
2. rasterize diva-gis roads in gdal
2. use Proximity (Raster Distance) in QGIS to make distance raster: braz_osm_rds_dist.tif

## DEM & Precip
Reproject DEM and precip to correct CRS in QGIS (/processed_layers/datatype_location_102033.tif)

### Precip
Resample precip to be at correct resolution
```{r}
### Open precip files
ac_precip <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/processed_layers/ppt_ambcar_102033.tif")
j_precip <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/processed_layers/ppt_jaman_102033.tif")

### Resample to match bol raster
ac_precip_resample <- raster::resample(ac_precip, 
                                         ac_2008, "bilinear")

### Resample to match braz raster
j_precip_resample <- raster::resample(j_precip, 
                                      j_2008, "bilinear")

### Write output rasters
writeRaster(ac_precip_resample,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/final/bol_precip.tiff",
            format = "GTiff")
writeRaster(j_precip_resample,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/final/bra_precip.tiff",
            format = "GTiff")

```

### DEM
Get slope and aspect rasters from QGIS
(datatype_location.tif)

Now want to downsample in gdal using 
gdalwarp -s_srs EPSG:102033 -t_srs EPSG:102033 -r near -of GTiff -tr 1 1 "C:\\Users\\Katherine Siegel\\Documents\\SESYNC\\dinamica\\processed_layers\\slope_ja
man.tif" "C:/Users/Katherine Siegel/AppData/Local/Temp/processing_02ef3f1f41ff4353ac5ac497de3127fb/e80dc7117b1749889b13e818c5c33439/OUTPUT.tif"

But there isn't enough disk space
```{r}


```


## Make base raster for gdal
```{r}
### Jamanxim
#### Open raster
j_2008 <- raster("D:/dinamica/brazil_simple/data/unsuper_bra_2008_dry_102033.tif")

#### Set all values to 1
values(j_2008) <- 1

#### Write output
writeRaster(j_2008,
            filename = "D:/dinamica/brazil_dinamica_data/bra_blank.tif",
            format = "GTiff")

### AmbCar
#### Open raster
ac_2008 <- raster("D:/dinamica/bolivia_simple/data/unsuper_bol_2008_dry_102033.tif")

#### Set all values to 1
values(ac_2008) <- 1

#### Write output
writeRaster(ac_2008,
            filename = "D:/dinamica/bolivia_dinamica_data/bol_blank.tif",
            format = "GTiff")
```

### Make raster stack
```{r}
ac_stack <- raster::stack(bpd_resample, 
                          ambcar_rios_resample, 
                          ambcar_rds_resample,
                          ambcar_pov_resample,
                          ambcar_cs_resample)

### Write out stack
writeRaster(ac_stack,
            "D:/dinamica/bolivia_simple/data/bolivia_static_vars.tif", 
            format = "GTiff")
```

