---
title: "dinamica_output"
author: "Katherine Siegel"
date: "August 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(rasterVis)
library(animation)
library(diffeR)
library(rgdal)
library(lme4)
# library(sf)

### Functions
### Functions
#### Function to check correlation
cor.prob <- function (X, dfr = nrow(X) - 2) {
  R <- cor(X, use="pairwise.complete.obs")
  above <- row(R) < col(R)
  r2 <- R[above]^2
  Fstat <- r2 * dfr/(1 - r2)
  R[above] <- 1 - pf(Fstat, 1, dfr)
  R[row(R) == col(R)] <- NA
  R
}
flattenSquareMatrix <- function(m) {
  if( (class(m) != "matrix") | (nrow(m) != ncol(m))) stop("Must be a square matrix.") 
  if(!identical(rownames(m), colnames(m))) stop("Row and column names must be equal.")
  ut <- upper.tri(m)
  data.frame(i = rownames(m)[row(m)[ut]],
             j = rownames(m)[col(m)[ut]],
             cor=t(m)[ut],
             p=m[ut])
}
```

## LUC Maps
### Bolivia
#### Open rasters
Open rasters of LUC from DINAMICA simulation
LC classes:  
* 0: no data  
* 1: forest (mountain)  
* 2: ag  
* 3: desert    
* 4: forest (lowland)  
```{r}
### Get list of files
bol_files <- list.files(path = "D:/dinamica/bolivia_simple/5_run_lucc",
                        pattern = "^Landscape", full.names = TRUE)

### Filter out non-.ers files
bol_files <- Filter(function(x) grepl("\\.ers$", x),
                    bol_files)

### Open maps as brick
brk <- do.call(brick, lapply(bol_files, raster))

# ### Open maps as stack
# stk <- do.call(stack, lapply(bol_files, raster))

# ### Convert all layers in brick to factor
# brk <- lapply(brk, as.factor)
```

#### Forest to ag conversions
* 0: no data  
* 1: forest (mountain)  
* 2: ag  
* 3: desert    
* 4: forest (lowland)
```{r}
### Extract 2008 layer
bol_08 <- brk[[1]]

### Reclassification matrix
reclass_df <- c(0, 0.9, NA, ## change NoData to NA
                0.9, 1.1, 1, ## mt forest = 1
                1.9, 2.1, 2, ## ag = 2
                2.9, 3.1, NA, ## desert to NA
                3.9, 4.1, 1) ## ll forest = 1
reclass_m <- matrix(reclass_df,
                ncol = 3,
                byrow = TRUE)

### Reclassify so all forest = 1, ag = 2, non-forest/non-ag = NA
bol_08_recl <- reclassify(bol_08, reclass_m)
# writeRaster(bol_08_recl, filename = "D:/dinamica/bolivia_simple/bol_2008_simulated.tif",
#             format = "GTiff")

### Reclassify entire brick
brk_recl <- reclassify(brk, reclass_m)

### Save rasterbrick
writeRaster(brk_recl, filename = "D:/dinamica/bol_simulated_landscapes_recl.tif",
            format = "GTiff")
```

### Reclassify actual LUC maps
```{r}
### Open files
bol_08_luc <- raster("D:/dinamica/bolivia_simple/data/unsuper_bol_2008_dry_102033.tif")
bol_18_luc <- raster("D:/dinamica/bolivia_simple/data/unsuper_bol_2018_dry_102033.tif")

### Reclassification matrix
reclass_df <- c(0, 0.9, NA, ## change NoData to NA
                0.9, 1.1, 1, ## mt forest = 1
                1.9, 2.1, 2, ## ag = 2
                2.9, 3.1, NA, ## desert to NA
                3.9, 4.1, 1) ## ll forest = 1
reclass_m <- matrix(reclass_df,
                ncol = 3,
                byrow = TRUE)

### Reclassify so all forest = 1, ag = 2, non-forest/non-ag = NA
bol_08_luc_recl <- reclassify(bol_08_luc, reclass_m)
bol_18_luc_recl <- reclassify(bol_18_luc, reclass_m)
```

#### Get random sample points
```{r}
### Open ambcar sf
ambcar <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/AmbCar/ambcarbuf_pr.shp")

### Get sample of points
ambcar_grid <- st_sample(ambcar, size = 10000, 
                         type = "random")

### Convert to spatial points
ambcar_pts <- as(ambcar_grid, "Spatial")

# ### Open bolivia raster brick
# bol_static <- brick("D:/dinamica/bolivia_simple/data/bolivia_static_vars_2.tif")

### Extract values
static_vals <- raster::extract(bol_static,
                               ambcar_pts,
                               df = TRUE)

### Rename layers
names(static_vals) <- c("ID", "crop_suit",
                        "dist_rds", "dist_rios",
                        "pop_dens", "precip",
                        "poverty", "bol_elev",
                        "bol_slope", "bol_aspect",
                        "dist_urb", "bol_protectedarea")

### Get LUC for t1 and t2
bol08_vals <- raster::extract(bol_08_luc_recl,
                               ambcar_pts,
                               df = TRUE)
bol18_vals <- raster::extract(bol_18_luc_recl,
                               ambcar_pts,
                               df = TRUE)
names(bol08_vals) <- c("ID", "luc_2008")
names(bol18_vals) <- c("ID", "luc_2018")

### Merge dfs
bol_data <- merge(bol08_vals, bol18_vals, by = "ID")
bol_data <- merge(bol_data, static_vals, by = "ID")
```

#### Subset to forest/ag transitions
```{r}
### Subset to forest in 2008
bol_data_ss <- subset(bol_data, luc_2008 == 1)

### Drop pts that turned to 0 in 2018
bol_data_ss <- subset(bol_data_ss, luc_2018 == 1 |
                        luc_2018 == 2)
```
forest = 1
ag = 2
#### Prep for regression
```{r}
### Want points that stayed forest to have "0" in 2018, deforested points to have "1"
bol_data_ss$luc_2018[bol_data_ss$luc_2018 == 1] <- "forest"
bol_data_ss$luc_2018[bol_data_ss$luc_2018 == 2] <- "ag"
bol_data_ss$luc_2018[bol_data_ss$luc_2018 == "forest"] <- 0
bol_data_ss$luc_2018[bol_data_ss$luc_2018 == "ag"] <- 1

### Set factor layers to factor
bol_data_ss$luc_2018 <- as.factor(bol_data_ss$luc_2018)
bol_data_ss$bol_protectedarea <- as.factor(bol_data_ss$bol_protectedarea)
bol_data_ss$ID <- as.factor(bol_data_ss$ID)
```

#### Regression
```{r}
luc_re <- glmer(luc_2018 ~ crop_suit + dist_rds + dist_rios +
                  pop_dens + poverty + precip +
                  bol_elev + bol_slope + bol_aspect +
                  dist_urb + bol_protectedarea + (1|ID),
                  data = bol_data_ss,
                  family = binomial(link = "logit"),
                  nAGQ = 0,
                  control = glmerControl(optimizer = "nloptwrap"))

### View summary
summary(luc_re)
```

#### Check correlations
```{r}
#### Forest subset
### Get cor table for continuous variables
cor_table_forest <- flattenSquareMatrix(cor.prob(bol_data_ss[, 4:13]))

### Look at vars with abs(cor.prob) > 0.66 and pvalue < 0.05
cor_table_forest <- subset(cor_table_forest, abs(cor) > 0.66 & p <= 0.05)
cor_table_forest

#### Full dataset
### Get cor table for continuous variables
cor_table <- flattenSquareMatrix(cor.prob(bol_data[, 4:13]))

### Look at vars with abs(cor.prob) > 0.66 and pvalue < 0.05
cor_table <- subset(cor_table, abs(cor) > 0.5 & p <= 0.05)
cor_table
```


## Visualize change
```{r}
### Extract 2008 and 2018 layers
bol_08 <- brk[[1]]
bol_18 <- brk[[10]]

### Convert to factors
bol_08 <- as.factor(bol_08)
bol_18 <- as.factor(bol_18)

# ### Map pixels that changed from 2008 vs 2018
# anychange <- brk[[10]] - brk[[1]]
# 
# ### Conver to factor
# anychange <- as.factor(anychange)
# rat <- levels(r)[[1]]
# rat[["landcover"]] <- c("land","ocean/lake", "rivers","water bodies")
# levels(r) <- rat
# 
# ## Plot
# levelplot(r, col.regions=rev(terrain.colors(4)), xlab="", ylab="")
```

### Summarize changes
```{r}
categoryComponentsPlot(bol_18, bol_08)
categorySourcesPlot(bol_18, bol_08)
```

## Reprojections
Reproject simulation maps from DINAMICA step 5 (for step 6)
```{r}
### Reproject BOL Landscape10
crs(bol_18) <- "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs"

### Write output
writeRaster(bol_18, filename = "D:/dinamica/bolivia_simple/5_run_lucc/Landscape10_prj.tif",
            format = "GTiff")
```

