---
title: "dinamica_prep"
author: "Katherine Siegel"
date: "April 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
library(stars)
```

## Amboro-Carrasco

### Shapefile of Amb-Car
```{r}
### Open shp of buffer
ambcar <- st_read("~/Documents/SESYNC/dinamica/case_study_shp/AmbCar/AmbCarBuf.shp")

### Transform to equal area projection (ESRI South America Equidistant Conic)
ambcar_pr <- st_transform(ambcar, crs = 102033)

### Add column for label
ambcar_pr$label <- 1

### Save ouput
st_write(ambcar_pr, 
         "~/Documents/SESYNC/dinamica/processed_layers/ambcar_proj.shp")
```


### Population density
```{r}
### Open shp of municipios
municip <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/pop_dens/municipios_339_pob2012.shp") %>% 
  st_transform(., crs = 102033)
st_write(municip, 
         "~/Documents/SESYNC/dinamica/bolivia_dinamica_data/pop_dens/municipios_339_pob2012_projected.shp")

### intersect pop density and PA polygon
ambcar_pd <- st_intersection(ambcar_pr, municip)
st_write(ambcar_pd, 
         "~/Documents/SESYNC/dinamica/processed_layers/bol_popdens.shp")
```
Converted this to raster using gdal in gitbash: 
gdal_rasterize -a densidad12 -tr 30 30 bol_popdens.shp bol_popdens.tiff

Made raster of population density in ArcMap (Polygon to Raster): pd_2012 (cell size = 30)
```{r}
bolpd <- raster("~/Documents/SESYNC/dinamica/bol_pd.tif")
```

### Rivers
#### Rios principales
Convert crs
```{r}
rios_princ <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_2002/rios_principales.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
rios_princ <- rios_princ %>%
  mutate(label = 1)

### Save projected version
st_write(rios_princ, "~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_2002/rios_principales_projected.shp")
```
Converted this to raster using gdal in gitbash: 
gdal_rasterize -a label -a_nodata 0 -tr 30 30 filename.shp filename.tiff

#### other code to convert to raster
```{r}
### Convert to raster
presence.absence.raster <- function(mask.raster, 
                                    env.data,
                                    raster.label = "") {
  require(raster)
  
  # set the background cells in the raster to 0
  mask.raster[!is.na(mask.raster)] <- 0
  
  # set the cells that contain rivers to 1
  env.raster <- rasterize(env.data, mask.raster, field = 1)
  env.raster <- merge(env.raster, mask.raster)
  
  #label the raster
  names(env.raster) <- raster.label
  return(env.raster)
}
```

#### Rios menores
Convert crs
```{r}
rios_men <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_menores/rios_menores.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
rios_men <- rios_men %>%
  mutate(label = 1)

### Save projected version
st_write(rios_men, "~/Documents/SESYNC/dinamica/bolivia_dinamica_data/rios/rios_menores/rios_menores_projected.shp")
```

### Roads
```{r}
### Open and reproject
boli_rds <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/roads_diva_gis/BOL_roads.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
boli_rds <- boli_rds %>%
  mutate(label = 1)

### Save projected version
st_write(boli_rds, "~/Documents/SESYNC/dinamica/processed_layers/boli_roads_projected.shp")
```

### Poverty rate
```{r}
### Open and reproject
boli_pobr <- st_read("~/Documents/SESYNC/dinamica/bolivia_dinamica_data/pobreza/nbi_vam_2012.shp") %>%
  st_transform(., crs = 102033) %>%
st_write(boli_pobr, 
         "~/Documents/SESYNC/dinamica/processed_layers/boli_pobr_projected.shp")
```

## Jamanxim

### Shapefile of Jamanxim
```{r}
### Open shp of buffer
jambuf <- st_read("~/Documents/SESYNC/dinamica/case_study_shp/JamanBuffer/JamanBuffer.shp")

### Transform to equal area projection (ESRI South America Equidistant Conic)
jambuf_pr <- st_transform(jambuf, crs = 102033)

### Save ouput
st_write(jambuf_pr, 
         "~/Documents/SESYNC/dinamica/processed_layers/jaman_proj.shp")
```

### Roads
```{r}
### Open and reproject
braz_rds <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/BRA_roads_divagis.shp") %>%
  st_transform(., crs = 102033)

### Add column for label for raster
braz_rds <- braz_rds %>%
  mutate(label = 1)

# ### Save projected version
# st_write(braz_rds, "~/Documents/SESYNC/dinamica/processed_layers/braz_roads_projected.shp")

### Crop to just include Para
braz <- getData('GADM', country = "Brazil", level = 1) %>%
  st_as_sf() %>%
  subset(., GID_1 == "BRA.14_1") %>%
  st_transform(., crs = 102033)
st_write(braz, 
         "~/Documents/SESYNC/dinamica/processed_layers/braz_para_bound.shp")
```
Cropped in gdal. Made tif of roads in Para using gdal.

### Pop density
```{r}
### Open file
braz_pd <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/popdens/para_pop_density.shp") %>%
  st_transform(., crs = 102033)

### Save output
st_write(braz_pd, "~/Documents/SESYNC/dinamica/processed_layers/braz_popdens_projected.shp")
```
Made tif of pop density in Para using gdal.

### Cities
Map of urban areas over 100k people from 2000
https://ww2.ibge.gov.br/home/geociencias/geografia/mapas_doc1.shtm
```{r}
### Open and reproject
urb <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/areas_urbanizadas_do_brasil_2005_ibge/AreasUrbanizadas_MunicipiosAcima100k_porMunicipio.shp") %>%
  st_transform(., crs = 102033)

### Save output
st_write(urb, "~/Documents/SESYNC/dinamica/processed_layers/braz_urban_projected.shp")
```
Crop urban layer to Para boundaries in gdal
ogr2ogr -clipsrc braz_para_bound.shp braz_para_urb.shp braz_urban_projected.shp

### Mines
```{r}
mines <- st_read("~/Documents/SESYNC/dinamica/brazil_dinamica_data/SIGMINE/PA.shp") %>%
  st_transform(., crs = 102033)

### Save output
st_write(mines,
         "~/Documents/SESYNC/dinamica/processed_layers/braz_mines_para_projected.shp")
```

## Global layer
### Crop suitability
```{r}
### Open crop suitability layer
crop_suit <- raster("~/Documents/SESYNC/dinamica/global_dinamica_data/overall_cropsuit_i_1981-2010.tif")

### Too big to project whole file, so need to crop to extent of buffers first 
crs(crop_suit)
```

#### Jamanxim
```{r}
### Open Jamanxim buffered shp
jaman <- st_read("~/Documents/SESYNC/dinamica/case_study_shp/JamanBuffer/JamanBuffer.shp")

### Project Jamanxim to match crs of crop_suit
# target_crs <- crs(crop_suit)
jaman_rpj <- st_transform(jaman, crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

### Make Jamanxim a sp object (raster doesn't work with sf)
jam_sp <- as(jaman_rpj, 'Spatial')

### Crop crops to Jamanxim
crop_jam <- crop(crop_suit, jam_sp)

### Project crop_jam to EPSG 102033
crop_jam_102033 <- projectRaster(crop_jam, 
                                 crs = "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs")

### Disaggregate raster so resolution matches 30x30
crop_jam_disag <- disaggregate(crop_jam_102033,
                               fact = c(30, 31))

### Make empty raster
empty_rast <- raster(ncol = 5550, nrow = 10230,
                     xmn = 380991.3, xmx = 549156.3,
                     ymn = 2670617, ymx = 2978177,
                     crs = "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs",
                     res = c(30, 30))

### Resample to get exact resolution
crop_jam_3030 <- resample(x = crop_jam_disag, 
                          y = empty_rast,
                          method = "bilinear")

### Write output
writeRaster(crop_jam_3030,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/crop_suit_jaman",
            format = "GTiff")
```
proj4string for 102033: +proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs

#### AmbCar
```{r}
### Open Amb buffered shp
ambcar <- st_read("~/Documents/SESYNC/dinamica/case_study_shp/AmbCar/AmbCarBuf.shp")

### Project AmbCar to match crs of crop_suit
ambcar_rpj <- st_transform(ambcar, crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

### Make AmbCar a sp object (raster doesn't work with sf)
ambcar_sp <- as(ambcar_rpj, 'Spatial')

### Crop crops to AmbCar
crop_ac <- crop(crop_suit, ambcar_sp)

### Project crop_jam to EPSG 102033
crop_ac_102033 <- projectRaster(crop_ac, 
                                 crs = "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs")

### Disaggregate raster so resolution matches 30x30
crop_ac_disag <- disaggregate(crop_ac_102033,
                               fact = c(28, 32))

### Make empty raster
empty_rast_ac <- raster(ncol = 9660, nrow = 6048,
                     xmn = -618682.5, xmx = -327157.5,
                     ymn = 1581007, ymx = 1763203,
                     crs = "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs",
                     res = c(30, 30))

######## Couldn't resample because not enough memory!!
### Resample to get exact resolution
crop_ac_3030 <- resample(x = crop_ac_disag, 
                          y = empty_rast_ac,
                          method = "bilinear")

### Write output
writeRaster(crop_jac_3030,
            filename = "~/Documents/SESYNC/dinamica/processed_layers/crop_suit_ambcar",
            format = "GTiff")
```
