---
title: "bolivia_dinamica_prep_2"
author: "Katherine Siegel"
date: "October 9, 2019"
output: html_document
---

## Description
Need to re-do clipping of Bolivia files to reflect new shapefile (Eva noticed error in original shp 9/27/2019). The new shapefile is larger than the old one, so will need to go back to larger data layers and clip them, rather than clipping the ones I already processed.

Store these files in new folder in external hard drive: bolivia_dinamica_data_9_27

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
library(lwgeom)
# library(stars)
```

## New case study polygon
```{r}
### Open shp of new buffer
ambcar <- st_read("D:/dinamica/bolivia_dinamica_data/AmbCar_Buffer_9_27/Bol_buffer.shp") %>%
  st_transform(., crs = 102033)

### Save reprojected buffer
st_write(ambcar,
         "D:/dinamica/bolivia_dinamica_data_9_27/bol_buff_pr.shp")

### New case study raster
### Used file from NextCloud: Remote sensing --> Semi-final classifications
### Reprojected to 102033 in QGIS
ambcar_rast <- raster("D:/dinamica/bolivia_dinamica_data_9_27/bol_2018_class.tif")
```

## New layers
### Population density
```{r}
### Open shp of municipios (reprojected in dinamica_prep.Rmd)
municip <- st_read("D:/dinamica/bolivia_dinamica_data/pop_dens/municipios_339_pob2012_projected.shp")

### Intersect pop density and PA polygon
ambcar_pd <- st_intersection(ambcar, municip)
st_write(ambcar_pd,
         "D:/dinamica/bolivia_dinamica_data_9_27/bol_popdens.shp")

### Converted this to raster using gdal in gitbash: 
# gdal_rasterize -a densidad12 -tr 30 30 bol_popdens.shp bol_popdens.tiff

### Open raster to resample to match LUC map
ambcar_pd_r <- raster("D:/dinamica/bolivia_dinamica_data_9_27/bol_popdens.tiff")

### Resample
bpd_resample <- raster::resample(ambcar_pd_r, 
                                 ambcar_rast, 
                                 "bilinear")

### Save resampled output
writeRaster(bpd_resample,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/bol_popdens_927.tiff",
            format = "GTiff")
```

### Rivers
Use rios menores file processed in dinamica_prep.Rmd
```{r}
### Make buffer around ambcar shp to use to clip rios menores shp
ambcar_buff <- st_buffer(ambcar, dist = 30000)

### Open rios menores shp
rios <- st_read("D:/dinamica/bolivia_dinamica_data/rios/rios_menores/rios_menores_projected.shp")

### Drop rivers outside buffered shp
rios_ambcar <- st_intersection(rios, ambcar_buff)

### Write out rios_ambcar so can calculate distance raster in Arc
st_write(rios_ambcar, 
         "D:/dinamica/bolivia_dinamica_data_9_27/ambcar_rios.shp")

### Calculate distance to rivers in Arc (set max distance to 12600 meters to capture variation)
### Then export as tif: riv_dist.tif

### Open tif
riv_dist <- raster("D:/dinamica/bolivia_dinamica_data_9_27/riv_dist.tif")

### Resample to match AC raster
ambcar_rios_resample <- raster::resample(riv_dist, 
                                         ambcar_rast,
                                         "bilinear")

### Save output raster
writeRaster(ambcar_rios_resample,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/bol_dist_rios_menores_927.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

### Roads
Use OSM layer from dinamica_prep.Rmd
```{r}
### Open and reproject
boli_rds <- st_read("D:/dinamica/bolivia_dinamica_data/roads_diva_gis/BOL_roads.shp") %>%
  st_transform(., crs = 102033)

### Make larger intersection buffer for roads (fewer roads than rivers)
ambcar_buff_large <- st_buffer(ambcar, dist = 50000)

### Intersect roads and ambcar buff
ambcar_rds <- st_intersection(boli_rds, 
                              ambcar_buff_large)

### Write out rios_ambcar so can calculate distance raster in Arc
st_write(ambcar_rds, 
         "D:/dinamica/bolivia_dinamica_data_9_27/ambcar_rds.shp")

### Calculate distance to rivers in Arc (set max distance to 50000 meters to capture variation)
### Then export as tif: rd_dist.tif

### Open tif
rd_dist <- raster("D:/dinamica/bolivia_dinamica_data_9_27/rd_dist.tif")

### Resample to match AC raster
ambcar_rds_resample <- raster::resample(rd_dist, 
                                         ambcar_rast,
                                         "bilinear")

### Save output raster
writeRaster(ambcar_rds_resample,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/bol_dist_rds_927.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

### Poverty rate
```{r}
### Open pov rate shp (reprojected in dinamica_prep.Rmd)
boli_pobr <- st_read("D:/dinamica/processed_layers/boli_pobr_projected.shp")

### Intersect with new shapefile
ambcar_pobr <- st_intersection(ambcar, boli_pobr)

### Save shp
st_write(ambcar_pobr,
         "D:/dinamica/bolivia_dinamica_data_9_27/bol_pov_rate.shp")

### Converted this to raster using gdal in gitbash: 
# gdal_rasterize -a p_pob_pobr -tr 30 30 bol_pov_rate.shp bol_pov_rate.tiff

### Open raster
ambcar_pov <- raster("D:/dinamica/bolivia_dinamica_data_9_27/bol_pov_rate.tiff")

### Resample to match ac_2008
ambcar_pov_resample <- raster::resample(ambcar_pov, 
                                        ambcar_rast,
                                        "bilinear")

### Save output raster
writeRaster(ambcar_pov_resample,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/bol_verty_927.tiff",
            format = "GTiff")
```

### Crop suitability
```{r}
### Project AmbCar to match crs of crop_suit
ambcar_rpj <- st_transform(ambcar, 
                           crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

### Make AmbCar a sp object (raster doesn't work with sf)
ambcar_sp <- as(ambcar_rpj, 'Spatial')

### Open crop suitability raster 
crop_suit <- raster("D:/dinamica/global_dinamica_data/overall_cropsuit_i_1981-2010.tif")

### Crop crops to AmbCar
crop_ac <- crop(crop_suit, ambcar_sp)

### Drop full raster
rm(crop_suit)

### Project crop_ac to EPSG 102033
crop_ac_102033 <- projectRaster(crop_ac, 
                                 crs = "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs")

### Resample raster to match ambcar_raster
crop_ac_3030 <- resample(x = crop_ac_102033, 
                         y = ambcar_rast,
                         method = "bilinear")

### Write output
writeRaster(crop_ac_3030,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/crop_suit_ambcar_927",
            format = "GTiff")
```

### Distance to cities
See methods in dinamica_prep.Rmd
```{r}
### Open raster of BOL dist to cities
bol_urb <- raster("D:/dinamica/processed_layers/bol_dist_urb_clip.tif")

### Resample to match ac_2008
bol_urb_resample <- raster::resample(bol_urb, 
                                     ambcar_rast, 
                                     "bilinear")

### Save output raster
writeRaster(bol_urb_resample,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/bol_dist_urb_927.tiff",
            format = "GTiff")
```

### Protected area status
Need original shapefiles from Eva to make this.

### Distance to mines
```{r}
### Open mining concession file
mines <- st_read("D:/dinamica/bolivia_dinamica_data/mining_concessions/Concesiones_mineras_2005.shp") %>%
  st_transform(., crs = 102033)

### Drop empty geoms
mines <- mines[!st_is_empty(mines), , drop = FALSE]

# ### Look at geometry types in the file
# mines_path <- "D:/dinamica/bolivia_dinamica_data/mining_concessions/Concesiones_mineras_2005.shp"
# class(st_geometry(st_read(mines_path, quiet = TRUE)))
# ## "sfc_POLYGON" "sfc"
# class(st_geometry(st_read(mines_path, quiet = TRUE, type = 3)))
# ## "sfc_POLYGON" "sfc"
# class(st_geometry(st_read(mines_path, quiet = TRUE, type = 1)))
# ## "sfc_GEOMETRY" "sfc"

### Make mines geometry valid
mines <- st_make_valid(mines)

### Make large buffer around ambcar shp to clip mines
ambcar_buff <- st_buffer(ambcar, dist = 60000)

### Drop mines outside buffered shp
mines_ambcar <- st_intersection(mines, ambcar_buff)

# plot(mines_ambcar[1])

### Write out mines_ambcar so can calculate distance raster in Arc
# st_write(mines_ambcar,
#          "D:/dinamica/bolivia_dinamica_data_9_27/mines_ambcar.shp")
### Issue with feature 392 (linestring)

### Add column for st_length (where length > 0, these should be the linestrings)
mines_ambcar <- mines_ambcar %>%
  mutate(mine_length = st_length(mines_ambcar))

### Look at linestring mine
mine_line <- subset(mines_ambcar, 
                    gml_id == "Concesiones_mineras_2005.6941")
plot(mine_line[1])

### Save file w/o mine_line
mines_subset <- subset(mines_ambcar, 
                       !gml_id == "Concesiones_mineras_2005.6941")
st_write(mines_subset,
         "D:/dinamica/bolivia_dinamica_data_9_27/mines_ambcar.shp")

### Get distance to mines in ArcGIS (max dist 52000)
### Export as tiff

### Open distance to mines tiff
mine_dist <- raster("D:/dinamica/bolivia_dinamica_data_9_27/mine_dist.tif")

### Resample to match AC raster
ambcar_mines_resample <- raster::resample(mine_dist, 
                                          ambcar_rast,
                                          "bilinear")

### Save output raster
writeRaster(ambcar_mines_resample,
            filename = "D:/dinamica/bolivia_dinamica_data_9_27/final/bol_dist_mines_927.tiff",
            format = "GTiff",
            overwrite = TRUE)
```

