---
title: "land use change"
author: "Katherine Siegel"
date: "February 26, 2020"
output: html_document
---

## Description
Play with LUC models in R

## Log
Getting issue with rasterizing prob_maps (making huge intermediate vectors that R can't allocate) -- try rasterizing in gdal directly.

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Open packages
library(tidyverse)
library(sf)
library(raster)
library(sp)
library(rgdal)
library(lulcc)
library(gsubfn)
library(caret)

### Remote sensing maps
bol_dat <- "D:/dinamica/bolivia_simple/data/"
bra_dat <- "D:/dinamica/brazil_simple/data/"
bol_dat_exp <- "D:/dinamica/bolivia_simple/data/ind_tifs"
```

## Grid sample
### Bolivia
```{r}
### Bolivia case study shape file
ambcar_shp <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/AmbCar/ambcar_buffer_updated.shp") %>%

  ### Convert to metric
  st_transform(crs = "+proj=utm +zone=20 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")

### Make sampling grid, point every 1 km
ambcar_samples <- ambcar_shp %>%
  
  ### Make samples
  st_make_grid(cellsize = c(1000, 1000), 
               what = "centers") %>%
  
  ### Convert to sf
  st_sf()  %>%
  
  ### Add identifiers
  mutate(lon = st_coordinates(.)[,1],
         lat = st_coordinates(.)[,2])

### Back to 102033
ambcar_samples <- ambcar_samples %>%
  st_transform(crs = 102033)
ambcar_shp <- ambcar_shp %>%
  st_transform(crs = 102033)

# ### Write out to check
# st_write(jaman_samples, "bra_pts_grid.shp")

### Remove points that fall outside of study area
ambcar_pts <- st_intersection(ambcar_samples,
                              ambcar_shp) 

### Convert pts to sp
ambcar_pts_sp <- as(ambcar_pts, "Spatial")
```

### Smaller area to practice on
```{r}
### Open shp subset
amb_imna <- st_read("amboro_imna.shp")

### Open raster brick
bol_stat_dat <- raster::brick(paste0(bol_dat,
                                "bolivia_static_vars.tif"))

### Clip raster brick to shp
bol_clip <- crop(bol_stat_dat, amb_imna)

### Save rasterbrick
writeRaster(bol_clip,
            filename = paste0(bol_dat,
                              "bol_vars_cl.tif"),
            format = "GTiff",
            overwrite = TRUE, 
            options = c("INTERLEAVE=BAND","COMPRESS=LZW"))

### Smaller remote sensing areas
### Open years
bol_2008 <- raster(paste0(bol_dat,
                          "classi_bol_dry_2008_102033.tif"))
bol_2018 <- raster(paste0(bol_dat,
                          "classi_bol_dry_2018_102033.tif"))

### Crop to IMNA
bol_2008 <- crop(bol_2008, amb_imna)
bol_2018 <- crop(bol_2018, amb_imna)

### Make reclassification df
reclass_df <- c(-1, 0.5, NA, # 0 -> No data
                0.6, 1.2, 1, # Keep ag = 1
                1.8, 2.4, 2, # Keep forest = 2
                2.5, 10, 3)  # All other land covers = 3 

### Convert to matrix                
reclass_m <- matrix(reclass_df,
                    ncol = 3,
                    byrow = TRUE)

### Reclassify rasters
bol_2008 <- reclassify(bol_2008, reclass_m)
bol_2018 <- reclassify(bol_2018, reclass_m)


### Write rasters
writeRaster(bol_2008,
             filename = paste0(bol_dat,
                               "lc_2008_clipped.tif"),
            format = "GTiff",
            overwrite = TRUE, 
            options = c("INTERLEAVE=BAND","COMPRESS=LZW"))
writeRaster(bol_2018,
             filename = paste0(bol_dat,
                               "lc_2018_clipped.tif"),
            format = "GTiff",
            overwrite = TRUE, 
            options = c("INTERLEAVE=BAND","COMPRESS=LZW"))
```


## lulcc package
Prep steps:  
1. Reclassify raster to drop land cover classes we aren't interested in

Steps:  
1. Load observed maps for both time periods (reclassify rasters to just have Ag, Forest, and Other)  
2. Calculate transition matrix  
3. Load explanatory variables  
4. Partition data into training and testing  
5. Write regression models  
6. Fit model to training data  
7. Map suitability of every pixel to different land use classes  


### Bolivia simple
```{r}
### Set observed maps
obs_bol <- ObsLulcRasterStack(x = bol_dat,
                              pattern = "*_clipped.tif",
                              categories = c(1, 2, 3),
                              labels = c("Agriculture",
                                         "Forest", "Other"),
                              t = c(0, 10))
# plot(obs_bol)

### Get transition matrix
tr_matrix <- crossTabulate(x = obs_bol,
                           times = c(0, 10))

### Open raster brick of explanatory variables
exp_vars <- raster::stack(paste0(bol_dat, "bol_vars_cl.tif"))
exp_vars <- ExpVarRasterList(exp_vars)

### Partition
part <- partition(x = obs_bol[[1]], 
                  size = 0.5, 
                  spatial = TRUE)

### Train data
train_data <- getPredictiveModelInputData(obs = obs_bol, 
                                          ef = exp_vars, 
                                          cells = part[["train"]])

### Write formulas for each land cover type
forms <- list(Agriculture ~ 1,
              Forest ~ bol_vars_cl.1 + bol_vars_cl.2 +
                bol_vars_cl.3 + bol_vars_cl.4 +
                bol_vars_cl.5 + bol_vars_cl.6 +
                bol_vars_cl.7 + bol_vars_cl.8 +
                bol_vars_cl.9 + factor(bol_vars_cl.10) +
                bol_vars_cl.11 + bol_vars_cl.12 +
                bol_vars_cl.13,
              Other ~ 1)

### Write GLMs
glm_models <- glmModels(formula = forms, 
                        family = binomial, 
                        data = train_data, 
                        obs = obs_bol)

### Extract data for suitability maps
all_data <- as.data.frame(x = exp_vars,
                          cells = part[["all"]])

### Make probability maps
prob_maps <- predict(object = glm_models,
                     newdata = all_data,
                     data.frame = TRUE)
points <- rasterToPoints(obs_bol[[1]], spatial = TRUE)
prob_maps <- SpatialPointsDataFrame(points, prob_maps)
prob_maps <- rasterize(x = prob_maps, y = obs_bol[[1]],
                      field = names(prob_maps))
levelplot(prob_maps)
```

### Demo code
```{r}
## Plum Island Ecosystems
## load data
data(pie)
## observed maps
obs <- ObsLulcRasterStack(x=pie,
                          pattern="lu",
                          categories=c(1,2,3),
                          labels=c("Forest","Built","Other"),
                          t=c(0,6,14))
obs
plot(obs)
crossTabulate(obs, times=c(0,14))
## explanatory variables
ef <- ExpVarRasterList(x=pie, pattern="ef")
ef
part <- partition(x=obs[[1]], size=0.1, spatial=TRUE)
train.data <- getPredictiveModelInputData(obs=obs, ef=ef, cells=part[["train"]])
forms <- list(Built ~ ef_001+ef_002+ef_003,
              Forest ~ ef_001+ef_002,
              Other ~ ef_001+ef_002)
glm.models <- glmModels(formula=forms, family=binomial, data=train.data, obs=obs)
rpart.models <- rpartModels(formula=forms, data=train.data, obs=obs)
rf.models <- randomForestModels(formula=forms, data=train.data, obs=obs)
## test ability of models to predict allocation of forest, built and other
## land uses in testing partition
test.data <- getPredictiveModelInputData(obs=obs, ef=ef, cells=part[["test"]])
glm.pred <- PredictionList(models=glm.models, newdata=test.data)
glm.perf <- PerformanceList(pred=glm.pred, measure="rch")
rpart.pred <- PredictionList(models=rpart.models, newdata=test.data)
rpart.perf <- PerformanceList(pred=rpart.pred, measure="rch")
rf.pred <- PredictionList(models=rf.models, newdata=test.data)
rf.perf <- PerformanceList(pred=rf.pred, measure="rch")
plot(list(glm=glm.perf, rpart=rpart.perf, rf=rf.perf))
## test ability of models to predict location of urban gain 1985 to 1991
part <- rasterToPoints(obs[[1]], fun=function(x) x != 2, spatial=TRUE)
test.data <- getPredictiveModelInputData(obs=obs, ef=ef, cells=part, t=6)
glm.pred <- PredictionList(models=glm.models[[2]], newdata=test.data)
glm.perf <- PerformanceList(pred=glm.pred, measure="rch")
plot(list(glm=glm.perf))
## obtain demand scenario
dmd <- approxExtrapDemand(obs=obs, tout=0:14)
matplot(dmd, type="l", ylab="Demand (no. of cells)", xlab="Time point",
        lty=1, col=c("Green","Red","Blue"))
legend("topleft", legend=obs@labels, col=c("Green","Red","Blue"), lty=1)
## get neighbourhood values
w <- matrix(data=1, nrow=3, ncol=3)
nb <- NeighbRasterStack(x=obs[[1]], weights=w, categories=2)
## create CLUE-S model object
clues.rules <- matrix(data=1, nrow=3, ncol=3, byrow=TRUE)
clues.parms <- list(jitter.f=0.0002,
                    scale.f=0.000001,
                    max.iter=1000,
                    max.diff=50,
                    ave.diff=50)
clues.model <- CluesModel(obs=obs,
                          ef=ef, models=glm.models,
                          time=0:14,
                          demand=dmd,
                          elas=c(0.2,0.2,0.2),
                          rules=clues.rules,
                          params=clues.parms)
## Create Ordered model
ordered.model <- OrderedModel(obs=obs,
                              ef=ef,
                              models=glm.models,
                              time=0:14,
                              demand=dmd,
                              order=c(2,1,3))
## perform allocation
clues.model <- allocate(clues.model)
ordered.model <- allocate(ordered.model, stochastic=TRUE)
## pattern validation
## CLUE-S
clues.tabs <- ThreeMapComparison(x=clues.model,
                                 factors=2^(1:8),
                                 timestep=14)
plot(clues.tabs)
plot(clues.tabs, category=1, factors=2^(1:8)[c(1,3,5,7)])
## Ordered
ordered.tabs <- ThreeMapComparison(x=ordered.model,
                                   factors=2^(1:8),
                                   timestep=14)
plot(ordered.tabs)
plot(ordered.tabs, category=1, factors=2^(1:8)[c(1,3,5,7)])
## calculate agreement budget and plot
## CLUE-S
clues.agr <- AgreementBudget(x=clues.tabs)
plot(clues.agr, from=1, to=2)
## Ordered
ordered.agr <- AgreementBudget(x=ordered.tabs)
plot(ordered.agr, from=1, to=2)
## calculate Figure of Merit and plot
## CLUE-S
clues.fom <- FigureOfMerit(x=clues.tabs)
p1 <- plot(clues.fom, from=1, to=2)
## Ordered
ordered.fom <- FigureOfMerit(x=ordered.tabs)
p2 <- plot(ordered.fom, from=1, to=2)

```

