---
title: "lulcc_brazil"
author: "Katherine Siegel"
date: "January 11, 2021"
output: html_document
---

## Description
Play with LUC models in Brazil

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Open packages
library(tidyverse)
library(sf)
library(raster)
library(sp)
library(rgdal)
library(lulcc)
library(gsubfn)
library(caret)

#### Function to check correlation
cor.prob <- function (X, dfr = nrow(X) - 2) {
  R <- cor(X, use="pairwise.complete.obs")
  above <- row(R) < col(R)
  r2 <- R[above]^2
  Fstat <- r2 * dfr/(1 - r2)
  R[above] <- 1 - pf(Fstat, 1, dfr)
  R[row(R) == col(R)] <- NA
  R
}
flattenSquareMatrix <- function(m) {
  if( (class(m) != "matrix") | (nrow(m) != ncol(m))) stop("Must be a square matrix.") 
  if(!identical(rownames(m), colnames(m))) stop("Row and column names must be equal.")
  ut <- upper.tri(m)
  data.frame(i = rownames(m)[row(m)[ut]],
             j = rownames(m)[col(m)[ut]],
             cor=t(m)[ut],
             p=m[ut])
}
```

## Land cover maps
Create stack with 2008 and 2018 maps, read it in
```{r}
### Load rasters of 2008 and 2018 land cover classes
# obs_lc <- ObsLulcRasterStack(x = braz_lc,
#                              categories = c(1, 2, 3, 
#                                             4, 5, 6),
#                              labels = c(),
#                              t = c(0, 10))

### Get transition matrix
# obs_change <- crossTabulate(x = obs_lc,
#                             times = c(0, 10))
```

## Steps from 2020 AAG Presentation
Regression models for different sets of variables for Brazil

### Sample on grid
```{r}
### Open buffer polygon
bra_buff <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/JamanBuffer/JamanBuffer_reproj.shp") %>%
  st_transform(., crs = "+proj=aea +lat_0=-32 +lon_0=-60 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0
+ellps=aust_SA +units=m +no_defs")

### Make sampling grid, point every 1 km
bra_samples <- bra_buff %>%
  
  ### Make samples (every 300 m)
  st_make_grid(cellsize = c(300, 300),
               what = "centers") %>%
  
  ### Convert to sf
  st_sf() %>%
  
  ### Add identifiers
  mutate(lon = st_coordinates(.)[, 1],
         lat = st_coordinates(.)[, 2])

### Add UID
bra_samples$uid <- 1:nrow(bra_samples)

### Open brazil 2008 map
bra_2008 <- raster("D:/dinamica/brazil_simple/data/classi_bra_dry_2008_102033.tif")

### Extract land cover type to sample points
bra_samples_2008 <- raster::extract(bra_2008, 
                                    bra_samples, 
                                    df = TRUE)

### See how many were forest in 2008
# b_2008_summ <- bra_samples_2008 %>%
#   group_by(classi_bra_dry_2008_102033) %>%
#   summarise(n_per_class = n())
### 0 = no data, 1 = agriculture, 2 = forest, 3 = bare soil, 4 = urban, 5 = wetland, 6 = desert, and 7 = water
### 279914 forested points in 2008

### Add uid back in
bra_samples_2008$uid <- bra_samples$uid

### Merge bra_samples_2008 with bra_samples
bra_samples <- merge(bra_samples, 
                     bra_samples_2008,
                     by = "uid")
rm(bra_samples_2008)

### Subset to forested points
bra_forest_samp <- bra_samples %>%
  subset(classi_bra_dry_2008_102033 == "2")

### Rename cols
bra_forest_samp <- bra_forest_samp %>%
  dplyr::select(uid, lon, lat, 
                lc_2008 = classi_bra_dry_2008_102033)

# ### Write out sample pts
# st_write(bra_forest_samp,
#          "D:/dinamica/sample_pts_model/bra_forest.shp")

### Open brazil 2018 map
bra_2018 <- raster("D:/dinamica/brazil_simple/data/classi_bra_dry_2018_102033.tif")

### Extract 2018 land cover class
luc_bra <- raster::extract(bra_2018, 
                           bra_forest_samp, 
                           df = TRUE)

### Add UID and merge with sf
luc_bra$uid <- bra_forest_samp$uid
luc_bra <- merge(bra_forest_samp, 
                 luc_bra,
                 by = "uid")

### Rename cols
luc_bra <- luc_bra %>%
  dplyr::select(uid, lon, lat, 
                lc_2008,
                lc_2018 = classi_bra_dry_2018_102033,
                geometry)

### Write out sample pts
st_write(luc_bra,
         "D:/dinamica/sample_pts_model/bra_forest.shp")

# ### Summarize transitions
# luc_bra_summ <- luc_bra %>%
#   group_by(lc_2018) %>%
#   summarise(n_transitions = n())
# luc_bra_summ <- luc_bra_summ %>%
#   mutate(portion_pts = n_transitions/279914*100)

### 94% of forested points remained in forest cover
### 4.9% converted from forest to ag
### 0.7% converted from forest to bare soil
### 0.3% converted from forest to wetland
### < 0.1% converted to urban or water

### Drop intermediate dfs/rasters
rm(bra_2008, bra_2018, bra_buff, bra_samples)

### OLD CODE
# ### Drop points that transitioned to other land uses
# luc_bol_fa <- luc_bol %>%
#   subset(classi_BOL_dry_2018 < 3)
# 
# ### Make sf
# st_geometry(luc_bol_fa) <- luc_bol_fa$geometry
# 
# ### Rename cols
# luc_bol_fa <- luc_bol_fa %>%
#   dplyr::select(uid, 
#                 lc_2008 = classi_BOL_dry_2008,
#                 lc_2018 = classi_BOL_dry_2018,
#                 lon, lat, geometry)
# 
# ### Save sf df
# st_write(luc_bol_fa, "bol_gridpts_for_regression.shp")
```

### UIDs of points with complete data
```{r}
### Open sample points
luc_bra <- st_read("D:/dinamica/sample_pts_model/bra_forest.shp")

### Open rasterbrick, all layers
bra_layers_all <- brick("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/brazil/discourse_analysis_final_layers/brazil_all_layers.tif")

### Extract values to pts
bra_dat_all <- extract(bra_layers_all, 
                       luc_bra,
                       df = TRUE)

### Rename columns
colnames(bra_dat_all) <- c("id", "aspect", "mines", 
                           "roads", "rivers", 
                           "cities", "elev", 
                           "popdens", "poverty", 
                           "ppt", "prot_status", 
                           "slope", "soil", 
                           "crop_suit", "field_res",
                           "paddd", "non_all_land",
                           "dist_ill_mines", "dist_ag",
                           "dist_fires", "fire_dens",
                           "dist_pr_rr",
                           "dist_pr_dams",
                           "agref_sett", "cattle")

### Give it a uid
bra_dat_all$uid <- luc_bra$uid

### Merge with sf
bra_dat_all <- merge(luc_bra,
                     bra_dat_all,
                     by = "uid")

### Version without geometry
bra_dat_all_simp <- bra_dat_all
bra_dat_all_simp$geometry <- NULL

### Drop incomplete rows
bra_dat_all_simp <- bra_dat_all_simp[complete.cases(bra_dat_all_simp), ]

### Drop rows where prot_status = 0 (??)
bra_dat_all_simp <- bra_dat_all_simp %>%
  filter(., !prot_status == "0")

### Get uids
uid_comp <- bra_dat_all_simp$uid

### Add geom back to visualize
# st_geometry(bol_dat_all) <- bol_dat_all$geometry
bra_dat_all <- bra_dat_all %>%
  filter(uid %in% uid_comp)

### Write out sample pts
st_write(bra_dat_all,
         "D:/dinamica/sample_pts_model/brazil_f_data.shp")

### Drop geom for regressions
bra_dat <- bra_dat_all
st_geometry(bra_dat) <- NULL

### Make column for transition/none
bra_dat <- bra_dat %>%
  mutate(transition = ifelse(lc_2018 == "2",
                             "no_change",
                             ifelse(lc_2018 == "1",
                                    "f_to_ag", 
                                    "other_change")),
         trans_rc = ifelse(transition == "no_change",
                           "0", ifelse(transition == "f_to_ag",
                                       "1", "2")))

### Make columns factor
fact_cols <- c("uid", "prot_status", 
               "paddd", "agref_sett",
               "lc_2018", "trans_rc")
bra_dat <- bra_dat %>%
  mutate_each_(funs(factor(.)), fact_cols)
```

### Check correlations
```{r}
### Make corr table
cor_table_bra <- flattenSquareMatrix(cor.prob(bra_dat[, c(2,3, 
                                                          7:15,
                                                          17:20,
                                                          22:28, 30)]))

### Look at vars with abs(cor.prob) > 0.66 and pvalue < 0.05
cor_table_bra <- subset(cor_table_bra, 
                        abs(cor) > 0.66 & p <= 0.05)

### Dist to cities and ppt (-0.7663484)
### Dist to cities and dist to illegal mines (0.6991763)
### Dist to cities and dist to proposed dams (0.9130546)
### Dist to illegal mines and dist to proposed dams (0.8404068)
### Dist to field research and dist to proposed railroads (0.6812415)
### Latitude and distance to cities (-0.9157438)
### Latitude and ppt (0.9009197)
### Latitude and distance to illegal mines (-0.8292653)
### Latitude and distance to proposed dams (-0.9992623)
### Longitude and distance to proposed RR (-0.7091224)
### Population density and % non-allocated land (0.9796182)
### Poverty rate and cattle (-0.9879367)
### ppt and distance to illegal mines (-0.8431194)
### ppt and distance to proposed dams (-0.9076312)
```

### Model 1
Standard LUC variables only


#### Regression
```{r}
### Run regression
fit_bol <- glm(trans_rc ~ aspect + slope + elev +
                 roads + rivers + mines +
                 crop_suit + popdens + poverty +
                 # (1|uid) +
                 lat + prot_status,
               data = bol_dat_red,
               family = binomial(link = "logit"))

### Write out coefficients
fit_bol_summ <- summary(fit_bol)
fit_bol_coeff <- as.data.frame(fit_bol_summ$coefficients)
write.csv(fit_bol_coeff, 
          file = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/analyses_aag/fit_bol_model1.csv")
```

### Model 2
Discourse analysis variables only

#### Assemble datasets
Extract values from rasterbricks to sample points
```{r}
# ### Open Bolivia rasterbrick, all layers
# bol_layers_all <- brick("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bolivia_all_vars.tif")
# 
# ### Extract values to pts
# bol_dat_2 <- extract(bol_layers_all, 
#                       bol_pts_sp,
#                       df = TRUE)
# 
# ### Rename columns
# colnames(bol_dat_2) <- c("id", "aspect", "mines", 
#                        "roads", "rivers", 
#                        "cities", "elev", 
#                        "popdens", "poverty", 
#                        "ppt", "prot_status", 
#                        "slope", "soil", 
#                        "crop_suit", "dist_ag", 
#                        "dist_fire", "fire_dens",
#                        "ill_mine", "field_res",
#                        "tourism", "pes")
# 
# ### Give it a uid
# bol_dat_2$uid <- bol_pts_sp$uid
# 
# ### Merge with sf
# bol_dat_2 <- merge(bol_dat_2, luc_bol_fa,
#                  by = "uid")
# 
# ### Open cow raster (head of cattle per area)
# cattle <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/bolivia/discourse_analysis_final_layers/bol_cows.tif")
# 
# ### Extract cattle
# bol_cattle <- extract(cattle, 
#                       bol_pts_sp,
#                       df = TRUE)
# 
# ### Give it a uid
# bol_cattle$uid <- bol_pts_sp$uid
# 
# ### Merge with rest of data
# bol_dat_2 <- merge(bol_dat_2, bol_cattle,
#                  by = "uid")
# 
# ### Make column for transition/none
# bol_dat_2 <- bol_dat_2 %>%
#   mutate(transition = ifelse(lc_2018 == "2",
#                              "no_change",
#                              "change"),
#          trans_rc = ifelse(transition == "no_change",
#                            "0", "1"))
# 
# ### Make columns factor
# fact_cols <- c("id", "prot_status", "pes", "lc_2008",
#                "lc_2018", "trans_rc")
# bol_dat_2 <- bol_dat_2 %>%
#   mutate_each_(funs(factor(.)), fact_cols)
# 
# ### Drop variables I don't need for model 2
# bol_dat_m2 <- bol_dat_2 %>%
#   dplyr::select(-aspect, -slope, -elev,
#                 -mines, -roads, -rivers,
#                 -cities, -popdens, -poverty,
#                 -ppt, -soil, -prot_status,
#                 -crop_suit)
```

#### Check correlations
Variables to include:
```{r}
### Make corr table
cor_table_bol <- flattenSquareMatrix(cor.prob(bol_dat[, c(5, 16:21,
                                                          25, 26, 28)]))

### Look at vars with abs(cor.prob) > 0.66 and pvalue < 0.05
cor_table_bol <- subset(cor_table_bol, 
                        abs(cor) > 0.66 & p <= 0.05)

### Highly correlated variables
### Distance to illegal mines and longitude (0.9691501)
### Distance to field research and latitude (0.7347974)

### Drop lon and lat

### Make updated dataset
bol_dat_red_m2 <- bol_dat %>%
  dplyr::select(-lon, -lat)
```

#### Regression
```{r}
### Run regression
fit_bol_m2 <- glm(trans_rc ~ roads +
                    dist_ag + dist_fire +
                    fire_dens + field_res +
                    ill_mine + tourism + pes +
                    bol_cows,
                  data = bol_dat_red_m2,
                  family = binomial(link = "logit"))

### Write out coefficients
fit_bol2_summ <- summary(fit_bol_m2)
fit_bol2_coeff <- as.data.frame(fit_bol2_summ$coefficients)
write.csv(fit_bol2_coeff, 
          file = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/analyses_aag/fit_bol_model2.csv")
```

### Model 3
All standard variables and discourse analysis variables

#### Check correlations
Use df bol_dat_2
```{r}
### Make corr table
cor_table_bol <- flattenSquareMatrix(cor.prob(bol_dat[, c(3:11, 
                                                          13:21, 
                                                          25, 26, 
                                                          28)]))

### Look at vars with abs(cor.prob) > 0.66 and pvalue < 0.05
cor_table_bol <- subset(cor_table_bol, 
                        abs(cor) > 0.66 & p <= 0.05)

### Highly correlated variables
### Distance to roads and cities (0.7254542)
### Distance to roads and precip (0.6751290)
### Poverty and soil moisture (0.7205976)
### Poverty and distance to illegal mining (-0.8114084)
### Soil moisture and distance to illegal mining (-0.9036921)
### Elev and field research (-0.6948379)
### Precip and field research (0.7440272)
### Distance to mines and tourism (0.6684893)
### Poverty and longitude (-0.7764958)
### Soil moisture and longitude (-0.9706443)
### Distance to illegal mining and longitude (0.9691501)
### Precip and latitude (0.8522991)
### Field research and latitude (0.7347974)

### Drop distance to cities (distance to roads), precip (roads, latitude), poverty (soil moisture, illegal mining), soil moisture (illegal mining, longitude), distance to field research (elev, precip, latitude), distance to legal mines (tourism), longitude

### Make updated dataset
bol_dat_red_m3 <- bol_dat %>%
  dplyr::select(-lon, -soil, -ppt,
                -cities, -poverty,
                -field_res, -mines)
```

#### Regression
```{r}
### Run regression
fit_bol_m3 <- glm(trans_rc ~ aspect + slope + elev +
                    roads + rivers +
                    popdens + prot_status +
                    crop_suit + 
                    dist_ag + dist_fire +
                    fire_dens + ill_mine + 
                    tourism + pes +
                    lat + bol_cows,
                  data = bol_dat_red_m3,
                  family = binomial(link = "logit"))

### Write out coefficients
fit_bol3_summ <- summary(fit_bol_m3)
fit_bol3_coeff <- as.data.frame(fit_bol3_summ$coefficients)
write.csv(fit_bol3_coeff, 
          file = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/analyses_aag/fit_bol_model3.csv")
```

### Model 4
Significant LUC variables + key DA variables:
* crop suitability, poverty rate, latitude, protection status, slope, aspect, elevation, distance to roads, rivers, mines  
* distance to northern and southern cities, fire perimeters, fire density, distance to roads, tourism, PES, cattle, land tenure


### Assemble data and check for correlations
```{r}
### Select variables for this model
bol_dat_4 <- bol_dat %>%
  dplyr::select(uid, crop_suit, poverty, prot_status, slope, aspect,
                elev, roads, mines, rivers, lat,
                dist_fire, fire_dens, tourism, pes, bol_cows,
                trans_rc)

### Make corr table
cor_table_bol <- flattenSquareMatrix(cor.prob(bol_dat_4[, c(2, 3, 5:14, 16)]))

### Look at vars with abs(cor.prob) > 0.66 and pvalue < 0.05
cor_table_bol <- subset(cor_table_bol, 
                        abs(cor) > 0.66 & p <= 0.05)

### Distance to legal mines correlated with distance to tourist sites (0.6684893)
bol_dat_4 <- bol_dat_4 %>%
  dplyr::select(-mines)
```

#### Regression
```{r}
### Run regression
fit_bol_m4 <- glm(trans_rc ~ aspect + slope + elev +
                    crop_suit + poverty +
                    prot_status + roads + 
                    rivers + lat +
                    dist_fire +
                    fire_dens + 
                    tourism + pes +
                    bol_cows,
                  data = bol_dat_4,
                  family = binomial(link = "logit"))

### Write out coefficients
fit_bol4_summ <- summary(fit_bol_m4)
fit_bol4_coeff <- as.data.frame(fit_bol4_summ$coefficients)
write.csv(fit_bol4_coeff, 
          file = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/analyses_aag/fit_bol_model4.csv")
```

### Compare model performance
```{r}
### AIC
AIC(fit_bol, fit_bol_m2,
    fit_bol_m3, fit_bol_m4)

### anova
anova(fit_bol, fit_bol_m2,
      fit_bol_m3, fit_bol_m4,
      test = "Chisq")
anova(fit_bol_m2, fit_bol_m3, test = "Chisq") ## 3 better than 2
anova(fit_bol_m3, fit_bol_m4, test = "Chisq") ## 4 better than 3
anova(fit_bol, fit_bol_m2, test = "Chisq")
anova(fit_bol, fit_bol_m4, test = "Chisq")

### Likelihood ratio test
lrtest(fit_bol, fit_bol_m3)
lrtest(fit_bol, fit_bol_m2)
lrtest(fit_bol_m2, fit_bol)

```