---
title: "peru_dinamica"
author: "Katherine Siegel"
date: "August 26, 2019"
output: html_document
---

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Packages
library(tidyverse)
library(raster)
library(sf)
```

## Protection status
Made shp of PAs and buffer in case_study_shp.Rmd.

Convert to raster in gdal
gdal_rasterize -a category -tr 30 30 peru_buffers.shp peru_buffers.tif
```{r}
### Open Peru LUC raster
peru_luc <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/remote_sensing/classi_per_dry_2008_102033.tif")

### Open file
prot_stat <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/case_study_shp/peru/peru_buffers.tif")

### Resample
prot_resample <- raster::resample(prot_stat, 
                                  peru_luc, 
                                  "ngb")

### Write out
writeRaster(prot_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_prot_status.tif",
            format = "GTiff",
            overwrite = TRUE)
```

## Categorical layers
Shapefiles from Aldo for locations of forest concessions, reforestation plots, nut production, PADDD, and protected forests.
```{r}
### Open shapefiles, convert to 102033 and write out
nuts <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/PermProd.shp") %>%
  st_transform(., crs = 102033)
nuts$category <- "1"
st_write(nuts, 
         "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/nut_prod.shp")

paddd <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/NP_changes.shp") %>%
  st_transform(., crs = 102033) 
paddd$category <- "1"
st_write(paddd, 
           "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/paddd.shp")

prot_for <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/ProtectedForest.shp") %>%
  st_transform(., crs = 102033)
prot_for$category <- "1"
st_write(prot_for, 
           "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/prot_forest.shp")

reforest <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/Reforestation.shp") %>%
  st_transform(., crs = 102033) 
reforest$category <- "1"
st_write(reforest, 
           "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/reforest.shp")

nonfor_conc <- st_read("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/NonForestryConcessions.shp") %>%
  st_transform(., crs = 102033) 
nonfor_conc$category <- "1"
st_write(nonfor_conc, 
           "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/nonforest_conc.shp")
```
rasterize in gdal, burn in to category

#### Resample to match map
```{r}
### Read in tifs
nuts <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/nut_prod.tif")
paddd <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/paddd.tif")
prot_forest <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/prot_forest.tif")
reforest <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/reforest.tif")
nonforest_conc <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/nonforest_conc.tif")

### Resample tifs
nuts <- raster::resample(nuts, 
                         peru_luc, 
                         "ngb")
paddd <- raster::resample(paddd, 
                          peru_luc, 
                          "ngb")
prot_forest <- raster::resample(prot_forest, 
                                peru_luc, 
                                "ngb")
reforest <- raster::resample(reforest, 
                             peru_luc, 
                             "ngb")
nonforest_conc <- raster::resample(nonforest_conc, 
                                   peru_luc, 
                                   "ngb")

### Write out tifs
writeRaster(nuts,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_nut_prod.tif",
            format = "GTiff",
            overwrite = TRUE)
writeRaster(paddd,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_paddd.tif",
            format = "GTiff",
            overwrite = TRUE)
writeRaster(prot_forest,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_prot_forest.tif",
            format = "GTiff",
            overwrite = TRUE)
writeRaster(reforest,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_reforest.tif",
            format = "GTiff",
            overwrite = TRUE)
writeRaster(nonforest_conc,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_nonforest_conc.tif",
            format = "GTiff",
            overwrite = TRUE)
```
### Precip
```{r}
### Read in
ppt <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/ppt_tambo_new.tif")

### Crop file
ppt_crop <- crop(ppt, extent(peru_luc))

### Resample
ppt_res <- raster::resample(ppt_crop, 
                            peru_luc, 
                            "bilinear")

### Write out
writeRaster(ppt_res,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_precip_new.tif",
            format = "GTiff",
            overwrite = TRUE)
```


## Classic model layers
### Convert to 102033
Use gdal to reproject all tifs from SESYNC/dinamica/peru_dinamica/ClassicModel
gdalwarp -t_srs EPSG:102033 -tr 30 30 -r bilinear ____.tif ____102033.tif

### Fix extent of all layers
```{r}
### Open Peru LUC raster
peru_luc <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/remote_sensing/classi_per_dry_2008_102033.tif")

################################  
### Soil
################################  
### Open soil raster
soil <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_soilm.tif")

### Resample soil raster to match Peru raster
soil_resample <- raster::resample(soil, peru_luc, "bilinear")

### Write out raster
writeRaster(soil_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_soilm.tif",
            format = "GTiff",
            overwrite = TRUE)

################################  
### Aspect
################################ 
### Open soil raster
aspect <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/aspect_102033.tif")

### Resample soil raster to match Peru raster
aspect_resample <- raster::resample(aspect, peru_luc, "bilinear")

### Write out raster
writeRaster(aspect_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_aspect.tif",
            format = "GTiff",
            overwrite = TRUE)

################################  
### Crop suit
################################ 
### Open raster
cropsuit <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/cropsuit_102033.tif")

### Resample soil raster to match Peru raster
cropsuit_resample <- raster::resample(cropsuit, peru_luc, "bilinear")

### Write out raster
writeRaster(cropsuit_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_cropsuit.tif",
            format = "GTiff",
            overwrite = TRUE)

################################  
### Distance to mines
################################ 
### Open raster
mines <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/d_mines_102033.tif")

### Resample soil raster to match Peru raster
mines_resample <- raster::resample(mines, peru_luc, "bilinear")

### Write out raster
writeRaster(mines_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_mines.tif",
            format = "GTiff",
            overwrite = TRUE)

################################  
### Distance to rivers
################################ 
### Open raster
rivers <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/d_rivers_102033.tif")

### Resample soil raster to match Peru raster
rivers_resample <- raster::resample(rivers, peru_luc, "bilinear")

### Write out raster
writeRaster(rivers_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_rivers.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(rivers)

################################  
### Distance to roads
################################ 
### Open raster
roads <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/d_roads_102033.tif")

### Resample soil raster to match Peru raster
roads_resample <- raster::resample(roads, peru_luc, "bilinear")

### Write out raster
writeRaster(roads_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_roads.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(roads)

################################  
### Distance to cities
################################ 
### Open raster
cities <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/d_urb_102033.tif")

### Resample soil raster to match Peru raster
cities_resample <- raster::resample(cities, peru_luc, "bilinear")

### Write out raster
writeRaster(cities_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_cities.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(cities)

################################  
### Distance to elevation
################################ 
### Open raster
elev <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/elev_102033.tif")

### Resample soil raster to match Peru raster
elev_resample <- raster::resample(elev, peru_luc, "bilinear")

### Write out raster
writeRaster(elev_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_elev.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(elev)

################################  
### National parks
################################ 
### Open raster
np <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/natparks_102033.tif")

### Resample soil raster to match Peru raster
np_resample <- raster::resample(np, peru_luc, "ngb")

### Write out raster
writeRaster(np_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_natpark.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(np)

################################  
### Pop density
################################ 
### Open raster
pd <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/popdens_102033.tif")

### Resample soil raster to match Peru raster
pd_resample <- raster::resample(pd, peru_luc, "bilinear")

### Write out raster
writeRaster(pd_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_popdens.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(pd)

################################  
### Poverty rate
################################ 
### Open raster
pov <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/povrate_102033.tif")

### Resample soil raster to match Peru raster
pov_resample <- raster::resample(pov, peru_luc, "bilinear")

### Write out raster
writeRaster(pov_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_poverty.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(pov)

################################  
### Precip
################################ 
### Open raster
precip <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/precip_102033.tif")

### Resample soil raster to match Peru raster
precip_resample <- raster::resample(precip, peru_luc, "bilinear")

### Write out raster
writeRaster(precip_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_precip.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(precip)

################################  
### Slope
################################ 
### Open raster
slope <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/ClassicModel/slope_102033.tif")

### Resample soil raster to match Peru raster
slope_resample <- raster::resample(slope, peru_luc, "bilinear")

### Write out raster
writeRaster(slope_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_slope.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(slope)
```

### Brick classic model layers
```{r}
### Open resampled layers
prot_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_prot_status.tif")
soil_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/new_dinamica_layers/peru/sm_peru_102033.tif")
aspect_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_aspect.tif")
cropsuit_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_cropsuit.tif")
mines_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_mines.tif")
rivers_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_rivers.tif")
roads_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_roads.tif")
cities_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_cities.tif")
elev_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_elev.tif")
pd_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_popdens.tif")
pov_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_poverty.tif")
precip_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_precip_new.tif")
slope_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_slope.tif")

### Make soil extent match the others
soil_resample <- raster::resample(soil_resample, 
                                  slope_resample,
                                  "bilinear")

### Make brick
peru_brick <- raster::brick(aspect_resample, 
                            cities_resample,
                            cropsuit_resample,
                            elev_resample,
                            mines_resample,
                            prot_resample,
                            pd_resample,
                            pov_resample,
                            precip_resample,
                            rivers_resample,
                            roads_resample,
                            slope_resample,
                            soil_resample)

### Write out brick
writeRaster(peru_brick, 
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_static_vars.tif", 
            format = "GTiff",
            overwrite = TRUE, 
            options = c("INTERLEAVE=BAND","COMPRESS=LZW"))
```

## Discourse analysis model layers
### Convert to 102033
Use gdal to reproject all tifs from SESYNC/dinamica/peru_dinamica/NewLayers
gdalwarp -t_srs EPSG:102033 -tr 30 30 -r bilinear ____.tif ____102033.tif

* assuming that the d_ layers are distance to __, so used bilinear method  
* didn't do distance to bare soil, wetlands because doesn't seem relevant  
* didn't do d_roads because already have that

### Fix extent of all layers
```{r}
################################  
### Distance to ag
################################  
### Open raster
ag <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_ag_102033.tif")

### Resample to match Peru raster
ag_resample <- raster::resample(ag, peru_luc, "bilinear")

### Write out raster
writeRaster(ag_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_ag.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(ag)

################################  
### Distance to control posts
################################  
### Open raster
control_posts <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_cntrlposts_102033.tif")

### Resample to match Peru raster
control_resample <- raster::resample(control_posts, peru_luc, "bilinear")

### Write out raster
writeRaster(control_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_controlposts.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(control_posts)

################################  
### Distance to communities
################################  
### Open raster
commun <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_commun_102033.tif")

### Resample to match Peru raster
commun_resample <- raster::resample(commun, peru_luc, "bilinear")

### Write out raster
writeRaster(commun_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_communities.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(commun)

################################  
### Distance to fires
################################  
### Open raster
fires <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_fires_102033.tif")

### Resample to match Peru raster
fire_resample <- raster::resample(fires, peru_luc, "bilinear")

### Write out raster
writeRaster(fire_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_fires.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(fires)

################################  
### Distance to forest
################################  
### Open raster
forest <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_forest_102033.tif")

### Resample to match Peru raster
forest_resample <- raster::resample(forest, peru_luc, "bilinear")

### Write out raster
writeRaster(forest_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_forest.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(forest)

################################  
### Distance to illegal mining
################################  
### Open raster
ill_min <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_ill_min_102033.tif")

### Resample to match Peru raster
ill_min_resample <- raster::resample(ill_min, peru_luc, "bilinear")

### Write out raster
writeRaster(ill_min_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_ill_mines.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(ill_min)

################################  
### Distance to minconc
################################  
### Open raster
minconc <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_minconc_102033.tif")

### Resample to match Peru raster
minconc_resample <- raster::resample(minconc, peru_luc, "bilinear")

### Write out raster
writeRaster(minconc_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_minconc.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(minconc)

################################  
### Distance to nonforconc
################################  
### Open raster
nonforconc <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_nonforconc_102033.tif")

### Resample to match Peru raster
nonforconc_resample <- raster::resample(nonforconc, peru_luc, "bilinear")

### Write out raster
writeRaster(nonforconc_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_nonforconc.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(nonforconc)

################################  
### Distance to npchg
################################  
### Open raster
npchg <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_npchg_102033.tif")

### Resample to match Peru raster
npchg_resample <- raster::resample(npchg, peru_luc, "bilinear")

### Write out raster
writeRaster(npchg_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_npchg.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(npchg)

################################  
### Distance to permprod
################################  
### Open raster
permprod <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_permprod_102033.tif")

### Resample to match Peru raster
permprod_resample <- raster::resample(permprod, peru_luc, "bilinear")

### Write out raster
writeRaster(permprod_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_permprod.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(permprod)

################################  
### Distance to protforest
################################  
### Open raster
protforest <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_protforest_102033.tif")

### Resample to match Peru raster
protforest_resample <- raster::resample(protforest, peru_luc, "bilinear")

### Write out raster
writeRaster(protforest_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_protforest.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(protforest)

################################  
### Distance to refor
################################  
### Open raster
refor <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_refor_102033.tif")

### Resample to match Peru raster
refor_resample <- raster::resample(refor, peru_luc, "bilinear")

### Write out raster
writeRaster(refor_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_refor.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(refor)

################################  
### Distance to tourism
################################  
### Open raster
tourism <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/NewLayers/d_tourism_102033.tif")

### Resample to match Peru raster
tourism_resample <- raster::resample(tourism, peru_luc, "bilinear")

### Write out raster
writeRaster(tourism_resample,
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_tourism.tif",
            format = "GTiff",
            overwrite = TRUE)
rm(tourism)
```

### Brick discourse analysis layers
```{r}
### Open resampled rasters
ag_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_ag.tif")
control_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_controlposts.tif")
commun_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_communities.tif")
fire_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_fires.tif")
forest_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_forest.tif")
ill_min_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_ill_mines.tif")
minconc_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_minconc.tif")
nonforconc_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_nonforest_conc.tif")
npchg_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_paddd.tif")
permprod_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_nut_prod.tif")
protforest_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_prot_forest.tif")
refor_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_reforest.tif")
tourism_resample <- raster("C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/per_tourism.tif")

### Convert NAs to 0 in concession layers
nonforconc_resample[is.na(nonforconc_resample[])] <- 0 
npchg_resample[is.na(npchg_resample[])] <- 0 
permprod_resample[is.na(permprod_resample[])] <- 0 
protforest_resample[is.na(protforest_resample[])] <- 0 
refor_resample[is.na(refor_resample[])] <- 0 

### Make brick
da_only_brick <- raster::brick(ag_resample,
                               control_resample,
                               commun_resample,
                               fire_resample,
                               forest_resample,
                               ill_min_resample,
                               minconc_resample,
                               nonforconc_resample,
                               npchg_resample,
                               permprod_resample,
                               protforest_resample,
                               refor_resample,
                               tourism_resample)

### Write out brick
writeRaster(da_only_brick, 
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/peru_da_vars.tif", 
            format = "GTiff",
            overwrite = TRUE, 
            options = c("INTERLEAVE=BAND","COMPRESS=LZW"))
```

### Brick all layers
Simple model layers + discourse analysis
```{r}
### Make brick
all_layer_brick <- raster::brick(aspect_resample, 
                                 cities_resample,
                                 cropsuit_resample,
                                 elev_resample,
                                 mines_resample,
                                 prot_resample,
                                 pd_resample,
                                 pov_resample,
                                 precip_resample,
                                 rivers_resample,
                                 roads_resample,
                                 slope_resample,
                                 soil_resample,
                                 ag_resample,
                                 control_resample,
                                 commun_resample,
                                 fire_resample,
                                 forest_resample,
                                 ill_min_resample,
                                 minconc_resample,
                                 nonforconc_resample,
                                 npchg_resample,
                                 permprod_resample,
                                 protforest_resample,
                                 refor_resample,
                                 tourism_resample)

### Write out brick
writeRaster(all_layer_brick, 
            filename = "C:/Users/Katherine Siegel/Documents/SESYNC/dinamica/peru_dinamica/data/peru_all_layers_new.tif", 
            format = "GTiff",
            overwrite = TRUE, 
            options = c("INTERLEAVE=BAND","COMPRESS=LZW"))
```
## OLD CODE
### Open raster layers
```{r}
### Get names of all files in folder
peru_layers <- list.files(path = "D:/Peru/TIffs/",
                          pattern = "*\\.tif$",
                          full.names = TRUE)
### Open all rasters
aspect <- raster(peru_layers[[1]])
cropsuit <- raster(peru_layers[[2]])
elev <- raster(peru_layers[[3]])
mines <- raster(peru_layers[[4]])
natparks <- raster(peru_layers[[5]])
popden <- raster(peru_layers[[6]])
pov <- raster(peru_layers[[7]])
rain <- raster(peru_layers[[8]])
rivers <- raster(peru_layers[[9]])
roads <- raster(peru_layers[[10]])
slope <- raster(peru_layers[[11]])
urban <- raster(peru_layers[[12]])
```

### Clip base layer to exclude BOL
Use elevation as base layer of rasters
```{r}
### Open new buffer shapefile
tam_bah <- st_read("D:/Peru/Buffer/Buffer.shp")
# plot(tam_bah[1])

### Crop elevation raster to new shp extent
elev_tambah <- raster::crop(elev, as.vector(st_bbox((tam_bah))))
plot(elev_tambah)
```


### Resample all rasters to match elev_tambah
```{r}
### Resample crop suitability
aspect_resample <- raster::resample(aspect, elev_tambah, "bilinear")
cs_resample <- raster::resample(cropsuit, elev_tambah, "bilinear")
mines_resample <- raster::resample(mines, elev_tambah, "bilinear")
natparks_resample <- raster::resample(natparks, 
                                      elev_tambah, "bilinear")
popden_resample <- raster::resample(popden, elev_tambah, "bilinear")
pov_resample <- raster::resample(pov, elev_tambah, "bilinear")
precip_resample <- raster::resample(rain, elev_tambah, "bilinear")
riv_resample <- raster::resample(rivers, elev_tambah, "bilinear")
rd_resample <- raster::resample(roads, elev_tambah, "bilinear")
slope_resample <- raster::resample(slope, elev_tambah, "bilinear")
urban_resample <- raster::resample(urban, elev_tambah, "bilinear")

### Make brick
peru_brick <- raster::brick(aspect_resample,
                            cs_resample, 
                            rd_resample, 
                            riv_resample,
                            urban_resample,
                            mines_resample,
                            popden_resample,
                            pov_resample,
                            natparks_resample,
                            precip_resample,
                            slope_resample,
                            elev_tambah)

### Write out brick
writeRaster(peru_brick, 
            filename = "D:/Peru/peru_static_vars.tif", 
            format = "GTiff",
            overwrite = TRUE, 
            options = c("INTERLEAVE=BAND","COMPRESS=LZW"))
```

